\documentclass[a4paper]{article}
\usepackage{standalone}
\usepackage{import}
\input{../../../../../newpreamble.tex}
% \usepackage{fourier}

\pagestyle{fancy} \fancyhf{}

\title{Math 230A: Homework 6}
\author{Lance Remigio}

\begin{document}
\maketitle    
\lhead{Math 230A: Homework 5}
\chead{Lance Remigio}
\rhead{\thepage}

\begin{problem}
    In class we proved that every \( 2- \)cell is a compact subset of \( \R^{2} \). Use the same procedure to prove that every closed and bounded interval \( [a,b] \) (that is, every \( 1- \)cell) is a compact subset of \( \R  \).
\end{problem}



\newpage

\ 

\newpage


\begin{problem}
    Complete the proof of Theorem 2.41, that is, let \( E \subseteq  \R^{k} \) and prove that if every infinite subset of \( E  \) has a limit point in \( E  \), then \( E  \) is closed and bounded.
\end{problem}

\newpage

\ 

\newpage
\begin{problem}
    Give an example of a metric space \( (Y,d) \) and a set \( E \subseteq Y \) where \( E  \) is closed and bounded but not compact.
\end{problem}

\newpage

\

\newpage


\begin{problem}
    Prove that a discrete space is \textbf{totally disconnected}. That is, prove that in a metric space equipped with the discrete metric, the only subsets are singletons and \( \emptyset \).
\end{problem}
\newpage

\

\newpage
\begin{problem}
    Let \( E \subseteq \R .  \) Prove that \( E  \) is connected if and only if it has the following property. If \( x \in E  \) and \( y \in E  \), and \( x < z < y  \), then \( z \in E  \).
\end{problem}
\newpage

\

\newpage
\begin{problem}
    Let \( (X,d) \) be a metric space. Let \( A  \) and \( B  \) be two connected subsets of \( X  \). Prove that if \( A \cap B \neq \emptyset  \), then \( A \cup B  \) is connected.
\end{problem}
\newpage

\

\newpage
\begin{problem}
    Recall that in class we mentioned that path-connectedness implies connectedness. Hence, every circle in \( \R^{2} \) is a connected subset of \( \R^{2} \). Use this fact to show that intersection of two connected sets in \( \R^{2} \) is not necessarily connected.
\end{problem}
\newpage 

\

\newpage
\begin{problem}
    \begin{enumerate}
        \item[(a)] If \( A  \) and \( B  \) are disjoint closed sets in some metric space \( (X,d) \), prove that they are separated. 
        \item[(b)] Prove the same for disjoint open sets.
        \item[(c)] Fix \( p \in X  \), \( \delta > 0  \), define \( A  \) to be the set of all \( q \in X  \) for which \( d(p,q) < \delta \), define \( B  \) similarly, with \( >  \) in place of \( <  \). Prove that \( A  \) and \( B  \) are separated.
        \item[(d)] Prove that every connected metric space with at least two points is uncountable. (Hint: Use (c)).
    \end{enumerate}
\end{problem}




\newpage 

\

\newpage




\begin{problem}
    Recall that in class we mentioned that implies connectedness. Hence, every closed disk in \( \R^{2} \) is a connected subset of \( \R^{2} \). Use this fact to show that the interior of a connected set in \( \R^{2} \) is not necessarily connected.
\end{problem}

\newpage 

\

\newpage


\begin{problem}
    Let \( (X,d) \) be a metric space. Suppose that \( E \subseteq X  \) is connected. Prove that \( \overline{E} \) is connected.
\end{problem}
\newpage 

\

\newpage
\begin{problem}
    Let \( (X,d) \) be a metric space. Prove that \( X  \) is connected if and only if \( \emptyset \) are the only subsets of \( X  \) which are both open and closed.
\end{problem}
\newpage 

\

\newpage
\begin{problem}
    Let \( E  \) be the set of all \( x \in [0,1] \) whose decimal expansion contains only the digits \( 4  \) and \( 7  \). Is \( E   \) countable? Is \( E  \) compact? Is \( E  \) perfect? (For this problem, you may use the fact that if \( x = 0.{x}_{1} {x}_{2} \cdots {x}_{n} \cdots \) is an element of \( E  \), then \( x = \sum_{ k=1  }^{ \infty   } \frac{ {x}_{k} }{  10^{k} }  \)).
\end{problem}
\newpage

\

\newpage


\begin{problem}
    Let \( (X,d) \) be a metric space.
        \begin{enumerate}
            \item[(a)] A subset of \( A \subseteq  X  \) is called \textbf{nowhere dense in \( X  \)} if the interior of the closure of \( A  \) is empty, that is \( (\overline{A})^{\circ} = \emptyset \). Prove that \( A  \) is nowhere dense if and only if \( A^{c} \) contains a dense open set in \( X  \).
            \item[(b)] Prove that if \( \R^{k} = \bigcup_{ n=1  }^{ \infty    } {F}_{n} \) where each \( {F}_{n} \) is a closed subset of \( \R^{k }  \), then at least one \( {F}_{n} \) is NOT nowhere dense.
        \end{enumerate}
\end{problem}

\newpage

\

\newpage


\end{document}
