\documentclass[a4paper]{article}
\input{../../../../../newpreamble.tex}
\title{Spectral Theorem For Bounded Self-Adjoint Opeartors on Hilbert Spaces}
\author{Lance Remigio}
\pagestyle{fancy}
\begin{document}
\maketitle
\lhead{Lance Remigio}
\chead{The Spectral Theorem}
\rhead{\thepage}
\tableofcontents

\begin{abstract}
This paper presents a generalization of the spectral theorem from finite-dimensional inner product spaces to the broader context of Hilbert spaces. We focus on the diagonalization of bounded self-adjoint linear operators, examining the structural and functional properties necessary for this extension. In particular, we investigate positive operators, their positive square roots, orthogonal projections, and the spectral families associated with such operators. These tools enable us to represent self-adjoint operators via Riemann–Stieltjes integrals. We conclude by applying the spectral theorem to diagonalize convolution operators, thereby revealing their structure as multiplication operators in the frequency domain. This not only simplifies their analysis but also highlights the deep connection between convolution, Fourier analysis, and the spectral properties of self-adjoint operators.
\end{abstract}

\section{Preliminary Results/Notation}

\import{prelim}{prelim.tex}

\section{Introduction}\label{section 2}

\import{intro}{intro.tex}

\section{Properties of Bounded Self-Adjoint Linear Operators}\label{section 3}

\import{hilbert_adjoint}{hil_adj.tex}

\section{Positive Operators}\label{section 4}

\import{positive_operators}{pos_op.tex}

\section{Projection Operators}\label{section 5}

\import{projection_operators}{proj_op.tex}

\section{Spectral Families}\label{section 6}

\import{spectral_families}{spec.tex}

\section{Spectral Theorem}\label{section 7}

\import{spectral_theorem}{spec_thm.tex}

\section{Conclusion}

    In this paper, we have carefully developed the foundational theory leading to the spectral representation of bounded self-adjoint linear operators on Hilbert spaces. Beginning with an examination of self-adjoint operators in finite-dimensional settings, we gradually introduced the necessary mathematical structures—including positive operators, square roots of operators, and orthogonal projections—to establish a framework conducive to generalization.

We then introduced the notion of a spectral family, whose properties allowed us to formulate a rigorous integral representation of our operator \( T \) using the Riemann-Stieltjes integral. This spectral representation serves as a powerful analytical tool, capturing the action of \( T \) through its interaction with a continuum of projection operators parameterized by the real line.

Finally, we explored an application of the spectral theorem by connecting it to convolution operators within the context of Fourier analysis. This demonstrated not only the theoretical elegance but also the practical significance of the spectral theorem in analyzing and diagonalizing important classes of operators in mathematical physics and signal processing.

The progression from discrete to continuous spectral decomposition exemplifies the power and reach of functional analysis, and underscores the importance of spectral theory in modern mathematical analysis.

\newpage

\begin{thebibliography}{999}
\bibitem{Kreyszig}
Erwin Kreyszig (1978) \emph{Introductory Functional Analysis with Applications} John-Wiley \& Sons. Inc.  

\bibitem{Rudin}
Walter Rudin (1987) \emph{Real and Complex Analysis}, Mcgraw-Hill 3rd ed.

\bibitem{Folland}
Gerald B. Folland (1992) \emph{Fourier Analysis and its Applications}, Wadsworth \& Brooks/Cole pp. 206-207

\bibitem{Stein}
Elias M. Stein \& Rami Shakarchi (2007) \emph{Fourier Analysis: An Introduction} Princeton University Press pp. 44-48

\end{thebibliography}

\end{document}

