\section{Continuous Functions on Compact Sets}
\subsubsection{Exercise 4.4.1}

\begin{enumerate}
    \item[(a)] Show that \( f(x) = x^3  \) is continuous on all \( c \in \R  \).
        \begin{proof}
Let \( \epsilon > 0  \) and let \( c \in \R  \). Choose \( \delta = \min \{ 1, \epsilon / | (c+1)^2 + (c+1)c + c^2 |   \}   \). Let \( f(x) = x^3  \). Then whenever \( | x - c  | < \delta  \), we have that 
\begin{align*}
    | f(x) - f(c)  | &= |  x^3 - c^3  |  \\
                     &=|x - c   | | x^2 + xc + c^2  | \\ 
                     &< \frac{ \epsilon  }{ | (c+1)^2 + (c+1)c + c^2 |  }  \cdot | (c + 1)^2 + (c + 1)c + c^2  |  \\
                     &= \epsilon.
\end{align*}
Hence, we have that \(\lim_{ x  \to c  } f(x) = f(c) \) for any \( c \in \R  \).
        \end{proof}
    \item[(b)] Argue, using Theorem 4.4.5, that \( f  \) is not uniformly continuous on \( \R  \).
        \begin{proof}
            Let \( (x_n) = n    \) and \( (y_n) = n + 1 / n   \), then 
            \[  | x_n - y_n | = \Big| \frac{ 1 }{ n }  \Big| \to 0.  \]
            Then we have that 
            \begin{align*}
                | f(x_n) - f(y_n)  | &= \Big| n^3 - \Big( n + \frac{ 1 }{ n }  \Big)^3  \Big|  \\
                                     &= \Big| - \Big( 3n + \frac{ 3 }{ n } + \frac{ 1 }{ n^3 } \Big) \Big| \\
                                     &= 3n + \frac{ 3 }{ n } + \frac{ 1 }{ n^3 } \\  
                                     &\geq 3.
            \end{align*}
            Hence, there exists \( \epsilon_0 = 3  \) such that \( | f(x_n) - f(y_n) | \geq \epsilon_0. \) which implies \( f(x) = x^3  \) is not uniform continuous.
        \end{proof}
    \item[(c)] Show that \( f \) is uniformly continuous on any bounded subset of \( \R  \). 
        \begin{proof}
            Let \( (a,b) \) be a bounded subset of \( \R  \). Then let \( \epsilon > 0 \). Let \( x,y \in [a,b] \). Choose \( \delta =  \). Hence, whenever \( | x - y  | < \delta  \) we have that 
            \begin{align*}
                | f(x) - f(y) | &= | x^3 - y^3  |  \\
                                &= | x - y  | | x^2 + xy + y^2  | \\
                                &< \delta \cdot 3b^2 \\ 
                                &= \frac{ \epsilon  }{ 3b^2 }  \cdot 3b^2 \\
                                &= \epsilon.
            \end{align*}
            Hence, we have that \( f \) is uniformly continuous on the bounded set \( (a,b) \subseteq \R  \).
        \end{proof}
\end{enumerate}

\subsubsection{Exercise 4.4.2} 
\begin{enumerate}
    \item[(a)] Is \( f(x) = 1 / x  \) uniformly continuous on \( (0,1) \)? 
        \begin{proof}[Solution]
        No it is not. Let \( (x_n), (y_n)  \) be two sequences such that \( x_n = 1 / 2n \) and \( y_n = 1 / (2n+1) \). Observe that \( | x_n - y_n  | \to 0  \) since both sequences tend to zero. Now we have that 
        \begin{align*}
            | f(x_n) - f(y_n) | &= | 2n - 2n - 1  |
                                = 1 = \epsilon_0.
        \end{align*}
        Hence, \( f(x)  \) is not uniformly continuous on \( (0,1) \).
        \end{proof}
    \item[(b)] Is \( g(x) = \sqrt{ x^2 + 1  }  \) uniformly continuous on (0,1)?
        \begin{proof}
        Let \( \epsilon > 0  \) and choose \( \delta = \epsilon. \) Assume \( f(x) \) is defined on \( (0,1)  \). Then whenever \( | x - y  | < \delta  \), we have that 
            \begin{align*}
                | g(x) - g(y) | &= | \sqrt{ x^2 + 1  } - \sqrt{ y^2 + 1  }  |  \\
                                &=  \frac{ | x^2 - y^2  |  }{ | \sqrt{ x^2 + 1  } + \sqrt{ y^2 + 1  }  |  }   \\
                                &=  \frac{ | x - y  | | x + y  |  }{ | \sqrt{ x^2 + 1  } + \sqrt{ y^2 + 1  }   |  }  \\  
                                &< \delta \cdot \frac{ | x+ y  |  }{ |  \sqrt{ x^2 + 1  } + \sqrt{ y^2 + 1  }   |  }  \\
                                &< \delta \cdot \frac{ 2 }{ 2 }  \\
                                &= \epsilon .
            \end{align*}
            Hence, we have that \( g(x)  \) is uniform continuous on \( (0,1) \subseteq \R  \).
        \end{proof}
\end{enumerate}


\subsubsection{Exercise 4.4.3} Show that \( f(x) = 1 / x^2  \) is uniformly continuous on the set \( [1, \infty  ) \) but not on the set \( (0,1] \).
\begin{proof}
    Let \( \epsilon > 0  \). Choose \( \delta = \delta / 2  \) such that whenever \( | x - y  | < \delta  \) for any \( x,y \in [1,\infty ) \) we have that 
    \begin{align*}
        | f(x) - f(y) | &= \Big| \frac{ 1 }{ x^2  } - \frac{ 1 }{ y^2  }  \Big|   \\
                        &= \frac{ | y^2 - x^2  |  }{  | x^2 y^2  |  } \\
                        &= \frac{ | x - y  | | x + y  |  }{ | x^2  | | y^2  |  }   \\
                        &\leq \frac{ | x - y  |  }{ | x^2  | | y^2  |  } (| x | + | y | ) \tag{Triangle Inequality}\\
                        &< \delta \cdot \frac{ 1 }{ | x^2 y^2  |  } (| x  | + | y | ) \tag{\( | x - y  | < \delta  \)}\\ 
                        &= \delta \cdot \Big( \frac{ 1 }{ x y^2  } + \frac{ 1 }{ x^2 y  }  \Big) \\
                        &< \frac{ \epsilon  }{ 2 }  \cdot 2 \tag{\( x \geq  1  \) \text{and} \( \delta = \epsilon / 2  \) } \\  
                        &= \epsilon.
    \end{align*}
    Hence, \( f(x) = 1 / x^2  \) is a continuous function on \( [1, \infty) \).
    Now we want to show that \( f(x) \) is not uniformly continuous on \( (0,1] \). Hence, let \( (x_n), (y_n) \) be two sequences that are contained in \( (0,1] \). Defined these two sequences as follows: 
    \begin{align*}
        x_n &= \frac{ 1 }{ \sqrt{ 2n }  },  \\
        y_n &= \frac{ 1 }{ \sqrt{ 2n + 1  }  }.
    \end{align*}
    Since \( (x_n) \) and \( (y_n) \) both tend towards zero, we have that \( | x_n - y_n  | \to 0  \). Now consider \( | f(x_n) - f(y_n) |  \). We want to construct an \( \epsilon_0  \) such that \( | f(x_n) - f(y_n) | \geq \epsilon_0  \). Hence, observe that 
    \begin{align*}
        | f(x_n) - f(y_n)  | &= \Big| \Big( \frac{ 1 }{ 1 / \sqrt{ 2n }  } \Big)^2  - \Big( \frac{ 1  }{ 1 / \sqrt{ 2n + 1  }  } \Big)^2   \Big|   \\
                             &= |  2n - 2n - 1  | \\
                             &= 1 \\
                             &= \epsilon_0.
    \end{align*}
    Hence, we have that \( f(x) \) cannot be uniformly continuous on the interval \( (0, 1] \).
\end{proof}



\subsubsection{Exercise 4.4.4} Decide whether each of the following statements is true or false, justifying each conclusion.

\begin{enumerate}
    \item[(a)] If \( f \) is continuous on \( [a,b] \) with \( f(x) > 0  \) for all \( a \leq x \leq b  \), then \( 1 /  f \) is bounded on \( [a,b] \) (meaning \( 1/ f \) has bounded range).
        \begin{proof}[Solution]
            Let \( f  \) be a continuous function \( [a,b] \) with \( f(x) > 0  \) for all \( a \leq x \leq b  \). Since \( [a,b] \) are compact sets, and \( f  \) is continuous on \( [a,b]  \), we have \( f(a) \leq f(x) \leq f(b) \). Since \( f > 0  \) for all \( a \leq x \leq  b  \), we have that 
            \[  \frac{ 1 }{ f(b) } \leq \frac{ 1 }{ f(x) } \leq \frac{ 1 }{ f(a) }   \]
            which means \( 1 / f   \) is a bounded function on \( [a,b] \).
        \end{proof}
    \item[(b)] If \( f \) is uniformly continuous on a bounded set \( A  \), then \( f(A) \) is bounded.
        \begin{proof}[Solution]
        Let \( f  \) be a uniformly continuous function on a bounded set \( A  \). Hence, let \( \epsilon  = 1  \). There exists \( \delta > 0  \) such that whenever \( | x - y  | < \delta  \), we have that 
        \[  | f(x) -f(y) | < \epsilon. \]
Since \( A  \) is bounded, there exists a subsequence \( (x_n) \to x  \) where \( x  \) is a limit point of \( A  \). Suppose for sake of contradiction that \( f(A) \) is unbounded. Let \( \delta = 1  \). Since \( f  \) is unbounded, we have that whenever \( | x_n - x_m  | <  1 \) where \(  n \neq m  \), we have 
    \[ | f(x_n) - f(x_m) | > 1.\]
    But this means that our function is not uniformly continuous on \( A  \) which is a contradiction. Thus, \( f  \) must have a bounded range.

        \end{proof}
    \item[(c)] If \( f  \) is defined on \( \R  \) and \( f(K) \) is compact whenever \( K  \) is compact, then \( f  \) is continuous on \( \R  \).
        \begin{proof}[Solution]
        This is false. Suppose we have the function \( f  \) defined as follows:
        \begin{align*}
            f(x) &= 
            \begin{cases}
                1 &\text{if } x \in \Q \\ 
                0 &\text{if } x \in \mathbb{I}.
            \end{cases} \\
        \end{align*}
        We have that for any compact set \( K  \), we have that every element of \( x  \) gets mapped to \( f(K) \) but \( f(x) \) is not a continuous function.
        \end{proof}
\end{enumerate}


\subsubsection{Exercise 4.4.5} Assume that \( g  \) is defined on an open interval \( (a,c) \) a nd it is known to be uniformly continuous on \( (a,b]  \) and \( [b, c) \). Let \( x \in (a,b] \) and \( y \in [b,c) \). Note that \( (a,c) = (a,b] \cup [b,c) \). Since \( f  \) is uniformly continuous on \( (a,b] \), we have that for any \( x, b \in (a,b] \), there exists \( \delta_1 > 0  \) such that whenever \( | x - b  | < \delta_2   \), we have that 
\[ | f(x) - f(b)  | < \frac{ \epsilon  }{ 2 } .\] Similarly, there exists \( \delta_2 > 0  \) such that whenever \( | b - y  | < \delta_2 \) such that whenever 
\[  | f(b) - f(y) | < \frac{ \epsilon  }{ 2 } . \]Choose \( \delta  =  \min \{ \delta_1, \delta_2  \}  \) such that whenever \( | x - y  | < \delta  \), we have that 
\begin{align*}
    | f(x) - f(y)  | &= | f(x) - f(b) + f(b) - f(y)  |  \\
                     &= | f(x) - f(b)  | + | f(b) - f(y) | \\
                     &< \frac{ \epsilon  }{ 2 } + \frac{ \epsilon  }{ 2 } \\ 
                     &= \epsilon.
\end{align*}
Hence, \( f(x)  \) is uniformly continuous on \( (a,c) \).





\subsubsection{Exercise 4.4.7} Prove that \( f(x) = \sqrt{ x  }  \) is uniformly continuous on \( [0,\infty ) \).
\begin{proof}
    Let \( \epsilon > 0  \) and let \( x, y \in [0, \infty ) \). If \( x,y = 0   \), then it immediately follows that \( f  \) is uniformly continuous since choosing \( \delta = \epsilon  \) implies that whenever \( | x - y  | < \delta  \), we have 
    \[ | f(x) - f(y) | = | \sqrt{ 0 } - \sqrt{ 0 }   | = 0 < \epsilon.   \]Suppose \( x,y \neq  0  \). Then choose \( \delta = \epsilon  \cdot 2\sqrt{ c  }  \) for any \( c \in [0, \infty)\) such that whenever \( | x - y  | < \delta  \) we have that
    \begin{align*}
        | f(x) - f(y)  | &= | \sqrt{ x } - \sqrt{ y }  |  \\
                         &= \Big| \frac{ x - y  }{ \sqrt{ x  } + \sqrt{ y }  }  \Big| \\
                         &= \frac{ | x - y  |  }{  \sqrt{ x  } + \sqrt{ y }    } \\
                         &\leq \frac{ | x - y  |  }{   2 \sqrt{ c }    }  \\
                         &< \frac{ \delta  }{ 2 \sqrt{ c }  }  \\
                         &= \epsilon. 
    \end{align*}
    Hence, we have that \( f(x)  = \sqrt{ x  }  \) is continuous on \( [0,\infty) \).
\end{proof}

\subsubsection{Exercise 4.4.8} Give an example of each of the following, or provide a short argument for why the request is impossible.
\begin{enumerate}
    \item[(a)] A continuous function defined on \( [0,1] \) with range \( (0,1) \).
        \begin{proof}[Solution]
        Let \( f(x) = 1 / x(x+1) \). The range of \( f(x) \) is \( (0,1) \).   
        \end{proof}
    \item[(b)] A continuous function defined on \( (0,1) \) with range \( [0,1] \).
        \begin{proof}[Solution]
        Let the following function \( f(x) \) be defined as follows:
        \[ f(x) = 
        \begin{cases}
            0 &\text{ if } x \in (0, \frac{ 1 }{ 4 } ) \\
            2x - \frac{ 1 }{ 2 } &\text{ if } x \in [ \frac{ 1 }{ 4 }, \frac{ 3 }{ 4 } ] \\
            1 &\text{ if } x \in (3/4, 1)
        \end{cases} \]
        \end{proof}
    \item[(c)] A continuous function defined on \( (0,1] \) with range \( (0,1) \).
        \begin{proof}[Solution]
        
        \end{proof}
\end{enumerate}


\subsubsection{Exercise 4.4.9}
\begin{tcolorbox}
    \begin{defn}[Lipschitz Functions]
        A function \( f: A \to \R  \) is called \textit{Lipschitz} if there exists a bound \( M > 0  \) such that 
        \[ \Big| \frac{ f(x) - f(y) }{ x - y  }   \Big| \leq M  \]
        for all \( x \neq y \in A  \).
    \end{defn}
\end{tcolorbox}
Geometrically speaking, a function \( f \) is Lipschitz if there is a uniform bound on the magnitude of the slopes of lines drawn through any two points on the graph of \( f \).

\begin{enumerate}
    \item[(a)] Show that if \( f: A \to \R  \) is Lipschitz, then it is uniformly continuous on \( A  \).
        \begin{proof}
        Suppose \( f: A \to \R  \) is Lipschitz and let \( x \neq y \in A  \). Let \( \epsilon > 0  \) and choose \( \delta = \epsilon / M  \). Assume \( | x - y  | < \delta  \). Using the fact that \( f  \) is Lipschitz, we have 
        \[ \Big| \frac{ f(x) - f(y)  }{ x - y  }   \Big| \leq M . \]
        But this is equivalent to 
        \[ | f(x) - f(y)  | \leq M | x - y  | < M \cdot \delta = M \cdot \frac{ \epsilon  }{ M  }  = \epsilon. \]
        Hence, we have that \( | f(x) - f(y) | < \epsilon  \) for all \( x \neq y \in A  \) implying that \( f: A \to \R   \) is a uniformly continuous function.
        \end{proof}
    \item[(b)] Is the converse statement true? Are all uniformly continuous functions necessarily Lipschitz?
        \begin{proof}[Solution]
        No the converse statement is not true. Take the function \( f(x) = \sqrt{ x  }  \). This function contains a slope that gets arbitrarly steep as the values of \( x  \) tend toward infinity. Another example is the function \( g(x) = 1 / x^2  \). We can see that if \( g(x)  \) is defined on \( (0,1 ) \) then the slope of the \( g(x)  \) gets arbitrary big as \( x \to 0  \).
        \end{proof}
\end{enumerate}

\subsubsection{Exercise 4.4.10} Assume that \( f \) and \( g  \) are uniformly continuous functions defined on a common domain \( A  \). Which of the following combinations are necessarily uniformly continuous on \( A  \):

\[ f(x) + g(x), ~ f(x)g(x), ~ \frac{ f(x) }{ g(x) }, ~ g \circ f (x).  \]


\begin{enumerate}
    \item[(a)] \( f(x) + g(x) \).
        \begin{proof}
        The addition of two uniformly continuous functions \( f(x), g(x) \) defined on the common domain \( A  \) is continuous. Let \( \epsilon > 0  \). Then define \( \delta = \min \{ \delta_1, \delta_2  \}  \) such that whenever 
        \begin{align*}
            | x - y  | &< \delta_1,  \\
            | x - y  | &< \delta_2 
        \end{align*}
        we have that 
        \begin{align*}
            | f(x) + g(x) - (f(y) - g(y)) | &= | (f(x) - f(y)) + (g(x) - g(y)) |  \\
                                            &\leq | f(x) - f(y)  | + | g(x) - g(y) | \\
                                            &< \frac{ \epsilon  }{ 2 } + \frac{ \epsilon  }{ 2 } \\
                                            &= \epsilon.
        \end{align*}
        Hence, the sum of two uniformly continuous functions is uniformly continuous.
        \end{proof}
    \item[(b)] \( f(x)g(x) \).
        \begin{proof}[Solution]
        Not necessarily true unless both of the functions are both bounded.

        \end{proof}
    \item[(c)] \( f(x) / g(x)  \) where \( g(x) > 0  \).
        \begin{proof}[Solution]
        Like the product of two uniformly continuous functions, the quotient is also not necessarily true unless both \( g(x) \) and \( f(x) \) are bounded below and above respectively.
        \end{proof}
    \item[(d)] \( f(g(x))  \).
        \begin{proof}
        Given \( f: A \to \R  \) and \( g:  A \to \R  \) uniformly continuous, assume that the range \( f(A) = \{ f(x) : x \in A  \}  \) is contained in \( A  \) so that composition is defined on \( A  \). Let \( \epsilon > 0  \). Let \( x \neq y \in A  \). Since \( f(x) \) is uniformly continuous on \( A  \), choose \( \epsilon  = \delta   \) such that whenever \( | f(x) - f(y)  | < \delta  \) and \( g : A \to \R  \) being uniformly continuous on \( A  \), we have that
        \begin{align*}
            | g \circ f (x) - g \circ f(y) | &= | g(f(x)) - g(f(y)) |  \\
                                             &< \epsilon.
        \end{align*}
        \end{proof}
\end{enumerate}


\subsubsection{Exercise 4.4.11 (Topological Characterization of Continuity).} Let \( g  \) be defined on all of \( \R  \). If \( B  \) is a subset of \( \R  \), define the set \( g^{-1}(B)  \) by 
\[  g^{-1}(B) = \{ x \in \R : g(x) \in B  \}. \]
Show that \( g  \) is continuous if and only if \( g^{-1}(O)  \) is open whenever \( O \subseteq \R  \) is an open set.
\begin{proof}
    \( (\Leftarrow) \) Let us construct an \( \epsilon - \)neighborhood around \( g(c) \); that is, \( V_{\epsilon }(g(c)) \). Suppose \( V_{\delta}(c) \) with \( x \in V_{\delta}(c) \). Since \( g^{-1}(O) \) is an open set, we have that \( V_{\delta}(c) \subseteq g^{-1}(O) \). But this means that \( x \in g^{-1}(O) \) implying that \( g(x) \in V_{\epsilon }(g(c))  \) since \( g(x) \in O  \).


    \( (\Rightarrow) \) Let \( V_{\epsilon }(g(c))  \) where \( c  \) is a limit point of \( O  \). Since \( g \) is a continuous function, there exists \( V_{\delta}(c)  \) such that whenever \( x \in V_{\delta}(c)  \), we have that \( g(x) \in V_{\epsilon}(g(c)) \). Since \( O  \) is an open set, we have that \( V_{\epsilon}(g(c)) \subseteq O  \). But this means that \( g(x) \in O  \) as well implying that \( x  \) is also an element of \( g^{-1}(O) \). Hence, we have that \( V_{\delta (c) }  \subseteq g^{-1}(O)\) and thus \( g^{-1}(O)  \) is an open set.
\end{proof}


