\documentclass[a4paper]{report}
\usepackage{standalone}
\usepackage{import}

\input{../../../../../newpreamble.tex}

\pagestyle{fancy}
\fancyhf{}

\begin{document}
    
\lhead{Math 234A}
\chead{Lance Remigio}
\rhead{\thepage}

\section{Lecture 6}

\subsection{Topics}

\begin{itemize}
    \item {\hyperref[Open Sets]{Open Sets}} 
    \item {\hyperref[Closed Sets]{Closed Sets}}
    \item {\hyperref[Interior Points]{Interior Points}} 
    \item {\hyperref[Closure of a set]{Closure of a set}} 
\end{itemize}

Let's recall the Euclidean metric on \( \C  \):
\[  d(z,w) = | \vec{ z }  - \vec{ w }   |.  \]
For real vector spaces, we can identify \( \C  \) with \( \R^{2} \) using the map \( \C \to \R^{2}  \) with \( \alpha + i \beta \to (\alpha, \beta) \). Thus, we can visualize \( \C  \) using \( \R^{2} \).

Recall that definition of continuity for functions in \( \R  \).

\begin{definition}[continuity in \( \R  \)]
    Let \( f: \R \to \R  \). We say that \( f  \) is \textbf{continuous} for each \( a \in \R  \) if for all \( \epsilon > 0 \), there exists \( \delta > 0  \) such that \( | x - a  |  < \delta \) implies
    \[  | f(x) - f(a) |  < \epsilon. \]
\end{definition}

Note that whenever we say \( | x - a  |  < \delta  \), we can also say that \( x \in (a - \delta, a + \delta) \). Similarly, we have \( | f(x) - f(a) | < \epsilon  \) is equivalent to \( f(x) \in (f(a) - \epsilon, f(a) + \epsilon) \).

\subsection{Open Sets} \label{Open Sets}

If we want to write the former using set notation, we can denote it as 
\[  \{ x \in \R : d(x,a) < \delta \}  \]
which is a more general statement than the one found in the definition above.
\begin{definition}[Open Ball]
  Consider the usual metric \( d(z,w) = | z - w  |   \) in \( \C  \). Let \( \epsilon > 0  \) and \( a \in \C  \). By an \textbf{open ball} centered at \( a  \), and radius \( \epsilon > 0  \), we mean the set
  \[ B(a,\epsilon)  =  \{ z \in \C : d(z,a) < \epsilon \}. \]
\end{definition}

\begin{definition}[Open Set]
   Let \( D \subseteq  \C .  \) We say \( D  \) is \textbf{open} if for each \( a \in D  \), we can find \( \epsilon > 0  \) such that  
   \(  B(a,\epsilon) \subseteq D  \).
\end{definition}

\begin{eg}
    \begin{enumerate}
        \item[(i)] \( \C  \) is open.
        \item[(ii)] Let \( \epsilon > 0  \) and \( a \in \C  \). Then \( B(a,\epsilon)  \) is also open; that is, open balls are open.
        \item[(iii)] Let \( {D}_{1} \) and \( {D}_{2} \) be open sets.
            Show that \( {D}_{1} \cap {D}_{2} \) is open. Let \( x \in {D}_{1} \cap {D}_{2} \) To show that \( {D}_{1} \cap {D}_{2} \) is open, we need to find \( \delta > 0  \) such that \( B(x,\delta) \subseteq {D}_{1} \cap {D}_{2} \). Since \( x \in {D}_{1} \cap {D}_{2} \), then \( x \in {D}_{1} \) and \( x \in {D}_{2} \). Since \( {D}_{1} \) and \( {D}_{2} \) are open sets, we can find \( \epsilon > 0  \) and \( \epsilon' > 0  \) such that 
            \begin{center}
               \( B(x,\epsilon) \subseteq {D}_{1} \) and \( B(x, \epsilon') \subseteq  {D}_{2} \), respectively. 
            \end{center} By definition, we see that \( d(x,p) < \epsilon \) for all \( p \in {D}_{1} \) and \( d(x,q) < \epsilon' \). Then pick \( \delta = \min \{ d(x,p), d(x,q) \}  \). Since \( x  \) is in both \( {D}_{1} \) and \( {D}_{2} \), we have that 
            \[  B(x,\delta) \subseteq  {D}_{1} \cap {D}_{2}. \]
            Hence, \( {D}_{1} \cap {D}_{2} \) is open.
        \item The empty set is open.
        \item Let \( \{ {D}_{\lambda}  \}_{\lambda \in \Lambda} \) be a collection of open ets, where \( \Lambda \) is an indexing set. Define the set
            \[  \bigcup_{ \lambda \in \Lambda }^{  }  {D}_{\lambda} = \{ z \in \C : z \in {D}_{\lambda} \ \text{for some} \ \lambda \in \Lambda \}. \]
            Show that \( \bigcup_{ \lambda \in \Lambda }^{  } {D}_{\lambda}  \) is also open.
    \end{enumerate}
\end{eg}


\subsection{Interior Points}\label{Interior Points}

\begin{definition}[Interior Point]
  Let \( D \subseteq \C \) and \( a \in D  \). We say that \( a  \) is an \textbf{interior point} of \( D  \) if we can find \( \epsilon > 0  \) such that \( B(a, \epsilon) \subseteq  D  \).
\end{definition}

\begin{prop}
    \( D  \) is open if and only if each \( a \in D  \) is an interior point of \( D  \).
\end{prop}

\begin{eg}
    Consider the following intersection 
    \[  \bigcap_{ n=1  }^{ \infty  }  B(0,1/n)   \tag{1} \]
    Let us compute (1). This is just the singleton \( \{ 0 \}  \). Show that \( \{ 0  \}  \) is not open. Note that the intersection of arbitrary many open sets may not be open. 
\end{eg}

\subsection{Closed sets}\label{Closed Sets}


\begin{definition}[Closed Set]
    We say \( A \subseteq \C   \) \textbf{closed} if its complement     
    \[  \C \setminus  A = \{ z \in \C : z \notin A  \}   \] is open.
\end{definition}
\begin{eg}
    Define a closed ball with center at \( a \in \C  \) and radius \( \epsilon > 0  \) by
    \[  \overline{B}(a, \epsilon) = \{ z \in \C : | z - a  | \leq \epsilon \}. \]
    Note that this is not the same thing as the closure of the open ball! Show that \( \overline{B}(a,\epsilon) \) is closed.
\end{eg}
\begin{eg}
    \begin{itemize}
\item For any \( a \in \C  \), we say that the singleton \( \{ a  \}   \) is closed.
\item If \( {A}_{1}, {A}_{2}, \dots, {A}_{n} \) are closed sets. Then 
    \[  \bigcup_{ i =1  }^{ n }  {A}_{i} \ \text{is also closed.} \]
    We can just show that the complement of this set is open.
\item Let \( \{ {A}_{\Lambda} \}_{\lambda \in \Lambda}   \) be a collection of closed sets. Define
    \[  \bigcap_{ \lambda \in \Lambda }^{  }  {A}_{\lambda} = \{ z \in \C : z \in {A}_{\Lambda} \ \forall \lambda \in \Lambda \},  \]
    then \( \bigcap_{  \lambda \in \Lambda }^{  } {A}_{\lambda } \) is closed.
\end{itemize}
\end{eg}

\begin{definition}[Boundary Points]
   Let \( D \subseteq  \C  \). We say \( a \in \C  \) is a \textbf{boundary point} of \( D  \) if for all \( \epsilon > 0  \), \( B(a,\epsilon) \cap D \neq \emptyset \) and \( B(a,\epsilon) \cap (\C \setminus  D ) \neq \emptyset  \); that is, \( B(a,\epsilon) \) intersects \( D  \) and \( \C \setminus  D   \) non-trivially.  
\end{definition}

\begin{eg}
   Any point on the circle \( \{ z \in \C : | z - a  | = \epsilon \}  \) is a boundary point of \( B(a,\epsilon) \), where \( \epsilon > 0  \).
\end{eg}

\begin{eg}[Boundary Points of Singletons]
    \begin{itemize}
  \item  Note that the boundary point of the singleton is just the singleton itself.
    \item Let \( D = \C \setminus  \{ a  \}  \). Just like the first item, the boundary points of this set is just \( \{ a  \}  \). 
    \end{itemize}
\end{eg}

\begin{definition}[Accumulation Point]
Let \( D \subseteq  \C . \) We say \( a \in \C  \) is an \textbf{accumulation point} of \( D  \) if for any \( \epsilon > 0  \),
\[  B(a,\epsilon) \cap (D \setminus  \{ a \} ) \neq \emptyset. \]

\end{definition}

\begin{eg}
    \begin{enumerate}
        \item[(i)] Let \( D = \C  \). Then \( \{ 0  \}  \) is an accumulation point of \( D  \).
        \item[(ii)] Let \( a  \) such that \( | a  |  = 1  \). Then \( a  \) is an accumulation point of \( D = \{ z : | z | < 1   \}  \).
        \item[(iii)] Let \( D = \{ 1,i \}  \). Then \( D  \) has no accumulation points.
        \item[(iv)] If \( D = \{ w  \}  \) for some nonzero \( w \in \C  \). Thus, \( D' = \emptyset \). That is, every singleton set contains no accumulation points. Furthermore, any finite set does not have any accumulation points.
        \item[(v)] Let \( D = \R  \). Then the accumulation points of \( D  \) is just \( \R  \) itself. That is, any point of \( \R  \) is an accumulation point.
        \item[(vi)] Let \( D = B(0,1) \). The accumulation points are contained in the following set: 
            \[  \overline{B}(0,1) = \{ z \in \C : | z  |  \leq 1  \}. \]
    \end{enumerate}
\end{eg}

Another way to define the set of accumulation points of \( D  \) is the following:
\[  \{ a \in \C : \forall \epsilon > 0 , B(a,\epsilon) \cap (D \setminus  \{ a \} ) \}. \]

\label{Closure of a set}

\begin{definition}[Closure]
    Let \( D \subseteq \C \). We denote the \textbf{closure of \( D \)} by \( \textbf{D} \) and define \( \overline{D} \) as 
    \[  \overline{D} = D \cup \{ x \in D : \forall \epsilon > 0  \  B(x,\epsilon) \cap D \neq \emptyset \}.  \]
\end{definition}

The closure is the smallest closed set that contains \( D  \)!

\begin{lemma}
    \begin{enumerate}
        \item[(i)] \( \overline{D} \) is closed in \( \C  \).
        \item[(ii)] The following statements are equivalent:
            \begin{enumerate}
                \item[(a)] \( a \in \C  \) is an accumulation point of \( D  \)
                \item[(b)] There is a sequence \( ({z}_{n}) \) with \( {z}_{n} \in D  \), \( {z}_{n} \neq a  \) for all \( n \in {\Z}_{+} \) and \( {z}_{n} \to a  \).
            \end{enumerate}
    \end{enumerate}
\end{lemma}

\begin{proof}
\textbf{Proof is in the homework!}
\end{proof}

\begin{definition}[Bounded]
    We say \( D \subseteq \C  \) is \textbf{bounded} if there exists \( R > 0  \) such that \( D \subseteq \overline{B}(0,R) \); that is, \( | z  |  \leq R  \) for all \( z \in D  \); that is, \( D \subseteq  \overline{B}(0,R) \).
\end{definition}






\end{document}
