\documentclass[11pt,a4paper]{book}
\input{../../../../../newpreamble.tex}
\usepackage{standalone}
\usepackage{import}

\begin{document}

\begin{definition}[Metric Space]
   A set \( X  \), whose elements we shall call \textit{points}, is said to be a \textit{metric space} if with any two points \( p  \) and \( q  \) of \( X  \) there is associated a real number \( d(p,q) \) called the \textit{distance} from \( p  \) to \( q  \), such that 
   \begin{enumerate}
       \item[(a)] \( d(p,q) > 0  \) if \( p \neq q  \); \( d(p,p) = 0  \);
        \item[(b)] \( d(p,q) = d(q,p) \);
        \item[(c)] \( d(p,q) \leq d(p,r) + d(r,q) \) for any \( r \in X  \).
   \end{enumerate}
\end{definition}

\begin{itemize}
    \item Suppose a subset \( Y  \) of \( X  \) is a metric space, with the same distance function.
    \item \( Y  \) must also be a metric space with the same distance function as \( X  \) (metric).
\end{itemize}

\begin{definition}[ ]
    \begin{itemize}
        \item By the \textit{segment} \( (a,b) \) we mean the set of all \( x \in \R  \) such that \( a < x < b \).
        \item We call an \textit{interval} \( [a,b] \) to mean the set of all \( x \in \R  \) such that \( a \leq x \leq b  \) for \( a,b \in \R  \) with \( a < b  \).
        \item We call a \textit{half-open interval} either \( [a,b) \) or \( (a,b] \) to mean \( a \leq x <  b  \) and \( a < x \leq b  \), respectively.
        \item We call a \textit{k-cell} to mean that if \( {a}_{i} < {b}_{i} \), for \( i = 1, \dots, k  \), the set of all points \( x = ({x}_{1}, {x}_{2}, \dots, {x}_{k }) \in \R^{k } \) whose coordinates satisfy \( {a}_{i} \leq {x}_{i} \leq {b}_{i} (1 \leq i \leq k ) \).  
        \item If \( x \in \R^{k}  \) and \( r > 0  \), the \textit{open} (or \textit{closed}) \textit{ball} \( B \) with center at \( x  \) and radius \( r  \) is defined to be the set
            \[ B(x,r) = \{ y \in \R^{k}: | y - x  | < r  \}  \]
            or alternatively, \( | y - x  | \leq  r  \).
        \item We call a set \( E \subset \R^{k} \) \textit{convex} if
            \[  \lambda x + (1 - \lambda) y \in E  \]
            whenever \( x,y \in E  \), and \(  0 < \lambda < 1  \).
    \end{itemize}
\end{definition}

\begin{definition}[ ]
    Let \( X  \) be a metric space. All points and sets mentioned below are understood to be elements and subsets of \( X  \).
    \begin{enumerate}
        \item[(a)] A \textit{neighborhood} of \( p  \) is a set \( {N}_{r}(p) \) consisting of all \( q  \) such that \( d(p,q) < r  \) for some \( r > 0  \). The number \( r  \) is called the \textit{radius} of \( {N}_{r}(p) \). 
        \item[(b)] A point \( p  \) is a \textit{limit point} of the set \( E  \) if \textit{every} neighborhood of \( p  \) contains a point \( q \neq p  \) such that \( q \in E  \).
        \item[(c)] If \( p \in E  \) and \( p  \) is not a limit point of \( E  \), then \( p  \) is called an \textit{isolated point} of \( E  \).
        \item[(d)] \( E  \) is closed if every limit point of \( E  \) is a point of \( E  \).
        \item[(e)] A point \( p  \) is an \textit{interior} point of \( E  \) if there is a neighborhood \( N  \) of \( p  \) such that \( N \subset E  \).
        \item[(f)] \( E  \) is \textit{open} if every point of \( E  \) is an interior point of \( E  \). 
        \item[(g)] The \textit{complement} of \( E  \) (denoted by \( E^{c} \)) is the set of all points \( p \in X  \) such that \( p \neq E  \).
        \item[(h)] \( E  \) is \textit{perfect} if \( E  \) is closed and if every point of \( E  \) is a limit point of \( E  \).
        \item[(i)] \( E  \) is \textit{bounded} if there exists a \( M \in \R  \) and \( q \in X  \) such that \( d(p,q) < M  \) for all \( p \in E  \).
        \item[(j)] \( E  \) is \textit{dense} in \(  X  \) if every point of \( X  \) is a limit point of \( E  \), or a point of \( E  \) (or both).  
    \end{enumerate}
\end{definition}

\begin{remark}
    In \( \R^{1} \), neighborhoods are segments and in \( \R^{2} \) neighborhoods are interiors of circles.
\end{remark}

\begin{theorem}[Neighborhoods are Open]
    Every neighborhood is an open set.
\end{theorem}

\begin{proof}
Let \( p \in X  \). Consider the neighborhood \( {N}_{r}(p)  \) for some \( r > 0  \). Let \( y \in X  \). Similarly, we can construct a neighborhood \( {N}_{h}(y) \) for some \( h > 0  \). Observe that the distance between \( p \) and \( y \)  is   
\[  d(p,y) = r - h. \]
Our goal is to show that \( {N}_{h}(y) \subset {N}_{r}(p)  \) in order for \( {N}_{r}(p) \) to be open. Let \( x \in {N}_{h}(y) \). Using the triangle inequality, we can see that 
\begin{align*}
    d(p,x) &\leq d(p,y) + d(y,x) \\
           &< (r - h) + h \\
           &= r.
\end{align*}
This tells us that \( x \in {N}_{r}(p) \), proving that \( {N}_{r}(p) \) is an open set.
\end{proof}

\begin{theorem}[ ]
    If \( p  \) is a limit point of a set \( E  \), then every neighborhood of \( p  \) contains infinitely many points of \( E  \).
\end{theorem}
\begin{proof}
Suppose for sake of contradiction that there exists a neighborhood \( N \) of \( p  \) which contains only a finite number of points of \( E  \). Let \( {q}_{1}, {q}_{2}, \dots, {q}_{n} \) be the points of \( N \cap E  \) such that \( {q}_{m} \neq p  \) for all \( m  \). Observe that
\[  r = \min_{1 \leq m \leq n} d(p, {q}_{m}) > 0 \]
since each \( d(p, {q}_{m}) > 0 \). Since each \( d(p, {q}_{m}) < {\delta}_{m }  \) and not \( d(p, {q}_{m}) = {\delta}_{m} \), we have that none of the \( {q}_{m} \in {N}_{r}(p) \) where \( {q}_{m} \neq p  \). So, \( p  \) must not be a limit point of \( E  \) which is a contradiction. Thus, every neighborhood of \( p \) must contain infinitely many points of \( E  \).
\end{proof}

\begin{corollary}
   A finite point set has no limit points. 
\end{corollary}

\begin{eg}[Examples of Closed, Open, Perfect, Bounded Sets]
   \begin{enumerate}
       \item[(a)] The set of all \( z \in \C  \) such that \( | z  |  < 1  \). \textbf{Open and Bounded}
        \item[(b)] The set of all \( z \in \C  \) such that \( | z  |  \leq 1  \). \textbf{Closed, Perfect, Bounded}  
        \item[(c)] A nonempty finite set. \textbf{(Closed, Bounded)}
        \item[(d)] The set of all integers. \textbf{(Closed)}
        \item[(e)] The set 
            \[ E =  \Big\{ \frac{ 1 }{ n } : n \in \N  \Big\}.  \]
            Note that no point of \( E  \) is a limit point of \( E  \); that is, there are no limit points contained in \( E  \). \textbf{Bounded}
        \item[(f)] The set of all complex numbers (that is, \( \R^{2} \)).
        \item[(g)] The segment \( (a,b) \). \textbf{(Bounded)}
   \end{enumerate}  
\end{eg}

Note that \( (g) \) is not open in \( \R^{1} \) but open in \( \R^{2} \).

\begin{theorem}[ ]
    Let \( \{ {E}_{\alpha} \}  \) be a (either finite or infinite) collection of sets \( {E}_{\alpha} \). Then
    \[  \Big(  \bigcup_{ \alpha } {E}_{\alpha}  \Big)^{c} = \bigcap_{ \alpha }^{  } ({E}_{\alpha}^{c}). \]
\end{theorem}

\begin{theorem}[ ]
    A set \( E  \) is open if and only if its complement is closed.
\end{theorem}
\begin{proof}
    For the forwards direction, let \( x  \) be a limit point of \( E^{c} \). Thus, for all neighborhoods \( N(x) \), \( N(x)  \) contains a point \( q \neq x  \) such that \( q \in E^{c}  \). Since \( E  \) is open, \( N(e) \subset E  \) for every \( e \in E  \). Since \( q \notin E^{c} \), \( q  \) must NOT be an interior point of \( E  \). Thus, \( x \in E^{c} \), proving that \( E^{c} \) is closed. 

   For the backwards direction, suppose \( E^{c} \) is closed. Let \( x \in E  \). Since \( E^{c} \) is closed, all the limit points of \( E^{c} \) must be contained in \( E^{c} \). But \( x \notin E^{c} \), so \( x  \) must not be a limit point of \( E^{c} \). Thus, there exists a neighborhood \( N(x)  \) such that \( N(x) \cap E^{c}  \) is empty. Thus, \( x  \) must be an interior point of \( E  \); that is, \( N(x) \subset E  \). Hence, \( E  \) must be open.  
\end{proof}

\begin{corollary}
   A set \( F  \) is closed if and only if its complement is open. 
\end{corollary}

\begin{theorem}[ ]\label{Theorem 2.24}
    \begin{enumerate}
        \item[(a)] For any collection \( \{ {G}_{\alpha} \}  \) of open sets, \( \bigcup_{ \alpha  }^{  }  {G}_{\alpha} \) is open.
        \item[(b)] For any collection \( \{ {F}_{\alpha} \} \) of closed sets, \( \bigcap_{  \alpha  }^{  }  {F}_{\alpha} \) is closed.
        \item[c] For any finite collection \( {G}_{1}, {G}_{2}, \dots, {G}_{n} \) of open sets \( \bigcap_{ i=1  }^{ n  } {G}_{i}   \) is open.
        \item[(d)] For any finite collection \( {F}_{1}, {F}_{2}, \dots, {F}_{n} \) of closed sets \( \bigcup_{ i=1  }^{ n }  {F}_{i} \) is closed.
    \end{enumerate}
\end{theorem}
\begin{proof}

\end{proof}

\begin{eg}
   \begin{itemize}
       \item The finiteness found in part (c) and (d) of the preceding theorem is essential.
        \item Suppose \( {G}_{n} = (-1/n, 1/n) \) for \( n \in \N \). We can see that \( {G}_{n} \) is an open subset of \( \R  \). But observe that 
            \[  G = \bigcap_{ n= 1  }^{  \infty   } (-1/n, 1/n)  \]
            only contains one point, namely \( 0  \), which implies that \( G  \) is not an open subset of \( \R  \).
   \end{itemize} 
\end{eg}

\begin{itemize}
    \item The intersection of an infinite collection of open sets \textbf{need not} be open.
    \item The union of an infinite collection of closed sets need not be closed.
\end{itemize}

\begin{definition}[Closure]
    If \( X  \) is a metric space, if \( E \subset X  \), and if \( E' \) denotes the set of all limit points of \( E  \) in \( X  \), then the \textit{closure} of \( E  \) is the set \( \overline{E} = E \cup E' \). 
\end{definition}

\begin{theorem}[ ]
   If \( X  \) is a metric space and \( E \subset X  \), then 
   \begin{enumerate}
       \item[(a)] \( \overline{E} \) is closed,
        \item[(b)] \( E = \overline{E} \) if and only if \( E  \) is closed.
        \item[(c)] \( \overline{E} \subset F  \) for every closed set \( F \subset X  \) such that \( E \subset F  \).
   \end{enumerate}
\end{theorem}
\begin{proof}

\end{proof}

\begin{definition}[Open Relative to \( Y \)]
    Suppose \( E \subset Y \subset X  \), where \( X  \) is a metric space. To say that the set \( X  \) is \textit{open relative} to \( Y  \) is to say that for each \( p \in E  \), there is an associated \( r > 0  \) such that \( q \in E  \) whenever
    \begin{center}
        \( d(p,q) < r  \) and \( q \in Y  \).
    \end{center}
\end{definition}

\begin{theorem}[ ]
    Suppose \( Y \subset X  \). A subset of \( Y  \) is open relative to \( Y  \) if and only if \( E = Y \cap G  \) for some open subset \( G  \) of \( X  \).
\end{theorem}

\begin{proof}
    For the forwards direction, suppose \( E  \) is open relative to \( Y  \). For each \( p \in E  \), there exists a positive number \( {r}_{p} \) such that \( q \in E  \) whenever
    \begin{center}
         \( d(p,q) < {r}_{p} \) and \( q \in Y \).
    \end{center}
    Let \( {V}_{p} \) be the set
    \[  \{ q \in Y : d(p,q) < {r}_{p} \}  \]
    by definition. Since each \( {V}_{p} \) is just a neighborhood, we know that each \( {V}_{p} \) has to be an open subset of \( X  \). Thus, we can set
    \[  G = \bigcup_{ p \in E  }^{  }  {V}_{p} \]
    which implies \( G  \) is open by part (a) of {\hyperref[Theorem 2.24]{Theorem 2.24}}. Since \( p \in {V}_{p} \) for all \( p \in E  \) and \( p \in Y  \) (since \( E \subset Y  \)), we have \( E \subset Y \cap G   \). (\textbf{This is using the result from set theory that states \( E \subset Y  \) and \( E \subset {V}_{p} \) implies \( E \subset Y \cap {V}_{p} \)}.)
    With our choice of \( {V}_{p} \), we can see that \( Y \cap {V}_{p} \subset E  \). Since each \( {V}_{p} \subset G   \), we see that \( Y \cap G \subset E  \), which shows that \( E = Y \cap G  \).

    For the backwards direction, suppose \(  E = Y \cap G  \) for some open subset of \( G  \) of \( X  \). Since \( G  \) is open, for every \( p \in E  \), we can construct a neighborhood \( {V}_{p} \) such that \( {V}_{p} \subset G   \). So, \( {V}_{p} \cap Y \subset E   \). Thus, \( E  \) is open relative to \( Y  \).  
\end{proof}




\end{document}
