\section{Functional Limits}


\subsection{Defining the Functional Limit}
Consider a function \( f: A \to \R  \). Suppose \( c  \) of \( A  \) is a limit point. From the last chapter, recall that the definition of a limit point is any \( \epsilon - \)neighborhood \( V_{\epsilon }(c) \) intersects \( A \setminus \{ c \}  \). In other words, \( c  \) is a limit point of \(  A \) if and only if \( c = \lim x_n \) for some sequence \( (x_n) \subseteq A  \) with \( x_n \neq c  \) for all \( n \in \N  \). Furthermore, it is important to keep in mind that limit points of \(  A \) do not necessarily belong to \( A  \) unless it is closed. 

If \( c  \) is a limit point of our domain \( A  \), then, we can state that 
\[ \lim_{x \to c }f(x) = L  \] is intended to convey that the values of \( f(x) \) gets arbitrarily close to \( L \) as \( x  \) is chosen arbitrarily close to \( c \). It is important to keep in mind that \( c \) need not be in the domain of \( A  \).

The structure of the definition of functional limits is as follows:
Given a sequence \( (a_n) \), the assertion that \( \lim a_n = L   \) implies that for every \( \epsilon - \)neighborhood \( V_{\epsilon }(L) \) centered at \( L \), we can find a point in a sequence say \( a_N \) after which all the terms of \( a_n \) fall in \( V_{\epsilon }(L) \). This is in response to an arbitrary choice of \( x \) in the domain where we have a \( \delta- \)neighborhood

\begin{tcolorbox}
    \begin{defn}[Functional Limit]
        Let \( f: A \to \R  \), and let \( c \) be a limit point of the domain \( A  \). We say that \( \lim_{ x \to c } f(x) = L   \) provided that, for all \( \epsilon > 0  \), there exists a \( \delta > 0  \) such that whenever 
        \[ 0 <  | x - c  | < \delta  \] (and \( x \in A  \)) it follows that 
        \[ | f(x) - L  | < \epsilon.  \]
    \end{defn}
\end{tcolorbox}

This is often referred to as the epsilon-delta definition of a functional limit. The statement
\[ | f(x) - L  | < \epsilon  \]
is equivalent to saying that \( f(x) \in V_{\epsilon }(L) \). Likewise, the statement 
\[  | x - c  | < \delta \] is true if and only if \( x \in V_{\delta}(c) \). Note that we imposed an additional restriction that \( | x - c  | > 0  \). This is because we don't want \( x = c  \). We can recast the definition above in terms of \( \epsilon- \)neighborhoods to help get a more geometric view of what is happening with these functional limits.

\begin{tcolorbox}
\begin{defn}
    Let \( c  \) be a limit point of the domain \( f: A \to \R  \). We say \( \lim_{ x \to c } f(x) = L  \) provided that for every \( \epsilon - \)neighborhood \( V_{\epsilon }(L)  \) of \( L \), there exists a \( \delta- \)neighborhood \( V_{\epsilon }(c) \) around \( c \) with the property that for all \( x \in V_{\delta}(c) \) different from \( c  \) (with \( x \in A  \)) it follows that \( f(x) \in V_{\epsilon }(L) \).
\end{defn}
\end{tcolorbox}

The reminder that we must have \( x \in A   \) ensures that every possible \( x \in A  \) must be a valid input for the function in question. Note that the appearance of \( f(x) \) in our definitions carries an implicit assumption that \( x  \) is always part of the domain of \( f \). There is no use for considering isolated points outside of \( A  \). Hence, we can always expect that functional limits will have \( x \in A  \) that approach the limit point of \( A  \) or \( \text{dom}(f) \).

\begin{ex}
\begin{enumerate}
    \item[(i)] Suppose we want to show that for \( f(x) = 3x + 1  \), we have 
        \[ \lim_{ x \to 2 } f(x) = 7. \]
        \begin{proof}
        Let \( \epsilon > 0  \). Consider \( | f(x) - 7  |  \). We want to show that whenever \( | x - 2  | < \delta \), that 
        \[  | f(x) - 7 | < \epsilon. \]
        Hence, observe that 
        \begin{align*}
            | f(x) - 7  | &= | (3x+1) - 7  |  \\
                          &= | 3x - 6  |  \\
                          &= 3| x - 2 | \\ 
                          &< 3 \delta. \\
        \end{align*}
        We can choose \( \delta = \epsilon / 3  \) such that 
        \[  | f(x) - 7  | < 3 \delta = 3 \frac{ \epsilon  }{ 3 } = \epsilon. \]
        Hence, we have that \( \lim_{ x \to 2 } f(x) = 7. \)
        \end{proof}
    \item[(ii)] Let's show that 
        \[  \lim_{ x \to 2  } g(x) = 4, \]
        where \( g(x) = x^2  \).
        \begin{proof}
        Let \( \epsilon > 0  \). Suppose \( 0 < | x - 2  | < \delta  \). Then 
        \begin{align*}
            | g(x) - 4  | &= | x^2 - 4  |  \\
                          &= | (x-2)(x+2) | \\
                          &= | x-2 | | x+2 |.\\
        \end{align*}
        Since \( |x + 2 | < \delta + 4   \), observe that for \( \delta = \min \{1, \epsilon / 5\}  \), we have 
        \begin{align*}
           | g(x) - 4  |  &= | x-2 | | x+2 |  \\
                          &< \delta \cdot (\delta + 4 ) \\
                          &= \frac{ \epsilon  }{ 5 } \cdot 5 \\
                          &= \epsilon.
        \end{align*}
        \end{proof}
\end{enumerate}
\end{ex}

\subsection{Sequential Criterion for Functional Limits}

\begin{tcolorbox}
    \begin{thm}[Sequential Criterion for Functional Limits]
    Given a function \( f: A \to \R  \) and a limit point \( c \) of \( A \), the following two statements are equivalent: 
    \begin{enumerate}
        \item[(i)] \( \lim_{ x \to c } f(x) = L. \)
        \item[(ii)] For all sequences \( (x_n) \subseteq A  \) satisfying \( x_n \neq c  \) and \( (x_n) \to c  \), it follows that \( f(x_n) \to L  \).
    \end{enumerate}
    \end{thm}
\end{tcolorbox}

\begin{proof}
    (i) \( \implies \) (ii) Suppose \( \lim_{ x  \to c } f(x) = L  \). Let \( \epsilon > 0  \). By assumption, we have a sequence \( (x_n) \to c  \). It immediately follows that for some \( N \in \N  \) such that for all \( n \geq N  \) that \( x_n \in V_{\delta}(c) \). Hence, \( f(x_n) \in V_{\epsilon }(L) \) by the Topological Definition of functional limits.
 
    (ii) \( \implies \) (i) Let \( (x_n) \subseteq A  \) satisfying \( x_n \neq c  \) and \( (x_n) \to  c \) such that \( f(x_n) \to L  \). Suppose for sake of contradiction that \( \lim_{ x \to c } f(x) \neq L  \). Hence, there exists \( \epsilon_0 \) such that for any \( \delta > 0  \) where \( | x_n -c  | < \delta \) that \( | f(x_n) - L  | \geq \epsilon_0 \). Let \( \delta = 1/n \) and suppose we pick \( x_n \in V_{\delta}(c) \) such that \( f(x_n) \notin V_{\epsilon }(L) \). But this implies that \( f(x_n) \not \to L  \) which contradicts our assumption that it is. Hence, it must be the case that (i) holds.
\end{proof}

\begin{tcolorbox}
    \begin{cor}[Algebraic Limit Theorem for Function Limits]
    Let \( f \) and \( g \) be functions defined on a domain \( A \subseteq \R  \), and assume \( \lim_{ x \to c } f(x) = L  \) and \( \lim_{ x \to c } g(x) = M  \) for some limit point \( c \) of \( A  \). Then, 
    \begin{enumerate}
        \item[(i)] \( \lim_{ x \to c } kf(x) = kL  \) for all \( k \in \R  \),
        \item[(ii)] \( \lim_{ x \to c } [f(x) + g(x)] = L + M, \)
        \item[(iii)] \( \lim_{ x \to c } [f(x)g(x)] = L \cdot M  \), and 
        \item[(iv)] \( \lim_{ x \to c } \frac{ f(x) }{ g(x)  } = \frac{ L }{ M }  \) provided that \( M \neq  0 \).
    \end{enumerate}
    \end{cor}
\end{tcolorbox}

\begin{proof}
Exercise 4.2.1.
\end{proof}


\begin{tcolorbox}
    \begin{cor}[Divergence Criterion for Functional Limits]
    Let \( f \) be a function defined on \( A  \) and let \( c  \) be a limit point of \( A  \). If there exists two sequences \( (x_n) \) and \( (y_n) \) in \( A  \) with \( x_n \neq  c \) and \( y_n \neq c  \) 
    \[  \lim x_n = \lim y_n = c \text{~but~} \lim f(x_n) \neq \lim f(y_n),  \]
    then we conclude that the functional limit \( \lim_{x \to c } f(x)  \) does not exist.
    \end{cor}
\end{tcolorbox}

\begin{ex}
Suppose we wanted to show that \( \lim_{ x \to 0 } \sin(1/x) \) does not exist. Set \( x_n = 1/2n\pi \) and \( y_n = 1 / (2n\pi + \pi/2 ) \), then 
\[  \lim x_n = \lim y_n = 0  \] but
\( \sin(1/x_n) = 0  \) for all \( n \in \N  \) while \( \sin(1/y_n) = 1  \). Thus, we have 
\[  \lim \sin(1/x_n) \neq \lim  \sin (1/y_n), \]
and thus we know that \( \lim_{x \to  0 } \sin(1/x)  \) does not exist.
\end{ex}

\subsection{Exercises}
\subsubsection{Exercise 4.2.1}

\begin{enumerate}
    \item[(a)] Supply the details for how Corollary 4.1.1.1 follows from the Sequential Criterion for Functional Limits in Theorem 4.1.1 and the Algebraic Limit Theorem for sequences proved in Chapter 2.

    \begin{proof}
    Let \( f \) and \( g \) be functions defined on a domain \( A \subseteq \R  \). Assume \( \lim_{ x \to c } f(x) = L  \) and \( \lim_{ x \to c } g(x) = M  \) for some limit point \( c  \) of \( A  \). By the Sequential Criterion for functional limits, let \( (x_n), (y_n) \subseteq A  \) such that \( (x_n) \to c  \) and \( (y_n) \to c  \) where \( x_n, y_n \neq c  \) implying that \(f(x_n) \to L   \) and \( g(y_n) \to M  \). By the Algebraic Limit Theorem, we can state that 
    \[  \lim [f(x_n) + g(y_n)]\lim f(x_n) + \lim g(y_n) = L  + M.\]
    Hence, we have that 
    \[  \lim_{ x \to c } [f(x) + g(x)] = L + M  \]
    by the Sequential Criterion for Functional Limits.
    \end{proof}
    \item[(b)] Now, write another proof of Corollary 4.1.1.1 part (ii) directly from Definition for functional limits without using the sequential criterion in Theorem 4.1.1.
    \begin{proof}
    We can also prove the addition rule for Functional Limits directly from the definition. Suppose \( \lim_{ x \to c } f(x) = L  \) and \( \lim_{ x \to c } g(x) = M  \). Then for some \( \delta > 0  \), suppose \( c  \) is a limit point of \( A  \) such that \( 0 < | x -c  | < \delta \). We want to show that for any arbitrary \( \epsilon > 0  \) that 
    \[  | (f(x) + g(x)) - (L + M) | < \epsilon.  \]
    Hence, choose \( \delta = \min \{ \delta_1, \delta_2  \}  \)
    \begin{align*}
        |(f(x) + g(x)) - (L + M)   | &= | (f(x) - L ) + (g(x) - M ) |  \\
       &\leq  | f(x) - L  |  + | g(x) - M  | \\ 
       &< \frac{ \epsilon  }{ 2  }  + \frac{ \epsilon  }{ 2 } \\
       &= \epsilon.
    \end{align*}
    Hence, we have 
    \[  \lim_{ x \to c } [f(x) + g(x)] = L + M.  \]
    \end{proof}
    \item[(c)] Repeat (a) and (b) for Corollary 4.1.1.1 part (iii).
    \begin{proof}
    Let \( (x_n), (y_n) \subseteq A  \) such that \( (x_n) \to c  \) and \( (y_n) \to c  \) for some limit point \( c  \) of \( A  \) where  we have 
    \( \lim f(x_n) = L   \) and \( \lim  g(y_n) = M  \). By the Algebraic Limit Theorem, we have that 
    \[ \lim [f(x_n)g(y_n)] = \lim f(x_n) \cdot \lim g(y_n) = L \cdot M. \]
   By the Sequential Criterion, this also means that 
   \[  \lim_{ x \to c } [f(x)g(x)] = L \cdot M. \]

    Now we can prove the same fact but this time we use only the Definition of functional limit.
    Let \( f: A \to \R  \). Suppose there exists \( \delta > 0  \) such that \( 0 < | x - c  | < \delta  \) where \( c  \) is a limit point of \( A  \). Let \( \epsilon > 0  \). Our goal is to show that 
    \[ | f(x)g(x) - LM  | < \epsilon. \]
    Since \( \lim_{ x \to c } f(x) = L  \) and \( \lim_{ x  \to c } g(x) = M  \), choose \( \delta = \min \{  \delta_1, \delta_2, \delta_3  \}  \) 
    \begin{align*}
        | f(x)g(x) - LM  | &= | f(x)g(x) - g(x)L + g(x)L - LM |  \\
                           &= | g(x)(f(x) - L ) + L (g(x) - M)  | \\ 
                           &\leq | g(x) | | f(x) - L  | + L | g(x) - M  |   \\
                           &< M + 1 \cdot \frac{ \epsilon  }{ 2(M + 1)  } + L \cdot \frac{ \epsilon  }{ 2L  } \\
                           &= \epsilon.
    \end{align*}
    Hence, we have that 
    \[  \lim_{ x \to c } f(x)g(x) = L M. \]
    \end{proof}
\end{enumerate}


\subsubsection{Exercise 4.2.2} For each stated limit, find the largest possible \( \delta- \)neighborhood that is a proper response to the given \( \epsilon  \) challenge.

\begin{enumerate}
    \item[(a)] \( \lim_{ x \to 3 } (5x - 6 ) = 9  \).
        \begin{proof}[Solution]
        Since \( \epsilon = 1  \), we know that 
        \[ | (5x-6) - 9  | < 1.\]
        To solve for \( \delta \), we do the following
        \begin{align*}
            | (5x - 6) - 9  | &= | 5 (x - 3 ) | < 1    \\
                              &= 5 | x - 3  | < 1 
        \end{align*}
        which implies that 
        \[  | x - 3  | < \frac{ 1 }{ 5 } = \delta. \]
        Hence, the largest possible \( \delta- \)neighborhood that is a proper response to the given \( \epsilon   \) challenge. 
        \end{proof}
    \item[(b)] \( \lim_{ x \to 4 } \sqrt{ x } = 2  \), where \( \epsilon = 1  \).
        \begin{proof}[Solution]
        Since \( \epsilon = 1  \), we know that 
        \[  | \sqrt{ x }  - 2  | < 1. \]
        To get our \( \delta \), we just do the following manipulations
        \begin{align*}
            \sqrt{ x } - 2   &< 1  \\
            \sqrt{ x } &< 3 \\
            x &< 9 \\
            | x - 4  | &< 5 = \delta. \\
        \end{align*}
        Hence, our \( \epsilon  \) response is \( \delta =  5  \).
        \end{proof}
    \item[(c)] \( \lim_{ x  \to \pi } [[x]] = 3 \), where \( \epsilon = 1  \). (The function \( [[x]] \) returns the greatest integer less than or equal to \( x  \).)
        \begin{proof}[Solution]
            Let \( \epsilon = 1  \). We want to generate a \( \delta > 0  \) that satisfies the \( \epsilon  \) challenge. Since \( [[\pi]] = 3  \), our max \( \delta- \)neighborhood can only have \( \delta = \pi - 3  \)
        \end{proof}
    \item[(d)] We have (c) but this time with \( \epsilon = .01 \).  
        \begin{proof}[Solution]
        It would still remain as \( \delta = \pi - 3  \).
        \end{proof}
\end{enumerate}

\subsubsection{Exercise 4.2.6} Decide if the following claims are true or false, and give short justifications for each conclusion.

\begin{enumerate}
    \item[(a)] If a particular \( \delta \) has been constructed as a suitable response to a particular \( \epsilon  \) challenge, then any smaller positive \( \delta \) will also suffice.
        \begin{proof}[Solution]
        This is true since \( \delta \) that has been constructed is the largest possible neighborhood that one can produce as a response to the \( \epsilon  \) challenge. 
        \end{proof}
    \item[(b)] If \( \lim_{ x \to a } f(x) = L  \) and \( a \) happens to be in the domain of \( f \), then \( f(a) = L  \).
        \begin{proof}[Solution]
        This is false. I have trouble thinking of an example. Will get back to this one soon. 
        \end{proof}
    \item[(c)] If \( \lim_{ x \to a } f(x) = L  \), then \( \lim_{ x \to a } 3[f(x) - 2 ]^2 = 3(L-2)^2 \).
        \begin{proof}[Solution]
        This is true based on the Algebraic Functional Limit Theorem.
        \end{proof}
    \item[(d)] If \( \lim_{ x \to a } f(x) = 0  \), then \( \lim_{ x\to a } f(x)g(x) = 0   \) for any function \( g \) (with domain equal to the domain of \( f \)).
        \begin{proof}[Solution]
        This is not true in general since we can easily produce \( g(x)  \) that is unbounded. For this to work, we would need \( g(x) \) to be bounded.
        \end{proof}
\end{enumerate}

\subsubsection{Exercise 4.2.7} Let \( g: A \to \R  \) and assume that \( f \) is a bounded function on \( A \) in the sense that there exists \( M > 0  \) satisfying \( | f(x) | \leq  M  \) for all \( x \in A  \). Show that if \( \lim_{ x \to c } g(x) = 0  \), then \( \lim_{ x \to c } g(x)f(x) = 0  \) as well.
\begin{proof}
Let \( g: A \to \R  \). Suppose \( \lim_{ x \to c } g(x) = 0   \) and suppose \( f(x) \) is bounded; that is, there exists \( M > 0  \) such that \( | f(x) | \leq M  \) for all \( x \in A  \). Using the Functional Limit Definition, suppose there exists \( \delta > 0  \) such that \( 0 < | x - c  | < \delta \). Hence, we have 
\begin{align*}
    | f(x)g(x) - 0  | &= | f(x) g(x) |  \\
                      &= | f(x) | | g(x) | \\
                      &\leq M | g(x) | \\
                      &< M \cdot \frac{ \epsilon  }{ M } \\
                      &= \epsilon.
\end{align*}
It follows from this that \( \lim_{ x \to c } f(x)g(x) = 0  \).
\end{proof}

\subsubsection{Exercise 4.2.9 (Infinite Limits).} The statement \( \lim_{ x \to 0 } 1/x^2 = \infty  \) certainly makes intuitive sense. To construct a rigorous definition in the challenge response style of Definition 4.1.1 for an infinite limit statement of this form, we replace the (arbitrarily small) \( \epsilon > 0  \) challenge with an (arbitrarily large) \( M > 0  \) challenge: 

\begin{tcolorbox}
\begin{defn}
We say \( \lim_{ x \to c } f(x) = \infty  \) to mean that for all \( M > 0  \), we can find a \( \delta > 0  \) such that whenever \( 0 < | x - c  | < \delta \), it follows that \( f(x) > M  \).
\end{defn}
\end{tcolorbox}
\begin{enumerate}
    \item[(a)] Show \( \lim_{ x \to 0 } 1/x^2 = \infty  \) in the sense described in the previous definition.
        \begin{proof}
        Let \( M > 0  \) and \( f(x) = 1/x^2 \). Choose \( \delta = 1 / \sqrt{ M }  \). Since \( 0 < | x  | < \delta \), we have 
        \[ x^2 < \delta^2 \iff \frac{ 1 }{ x^2 } > \frac{ 1 }{ \delta^2  }. \]
        But this means that 
        \[ f(x) = \frac{ 1 }{ x^2 } > \frac{ 1 }{ \delta^2 } = \frac{ 1 }{ 1/ M } = M. \]
        Hence, we have 
        \[  \lim_{ x \to 0 } f(x) = \infty. \]
        \end{proof} \item[(b)] Now, construct a definition for the statement \( \lim_{ x \to \infty  } f(x) = L  \). Show that \( \lim_{ x \to \infty  } 1/x = 0  \).
       \begin{tcolorbox}
       \begin{defn}
      Let \( f: A \to \R  \). We say \( \lim_{ x \to \infty  } f(x) = L  \) to mean for any \( \epsilon > 0  \), there exists \( x_0 \in A  \) where \( A \subseteq \R  \) such that for any \( x \geq x_0  \), we have 
      \[  | f(x) - L  | < \epsilon. \]
       \end{defn}
       \end{tcolorbox} 

       \begin{proof}[Solution]
        We start with some sketch work for what \( x_0  \) might be. Observe that 
        \begin{align*}
            | f(x) - L  | &= | \frac{ 1 }{ x } - 0  |  \\
                          &= \frac{ 1 }{ x } \\ 
                          &< \epsilon.
        \end{align*}
        Solving for \( x \), we get that 
        \[  x > \frac{ 1 }{ \epsilon  }.  \] Hence, \( x_0 = 1 / \epsilon   \).

        Let \( \epsilon > 0  \) and let \( f(x) = 1 / x  \). Choose \( x_0 = 1 / \epsilon  \). Suppose \( x > x_0 = 1 / \epsilon  \). Then we have that 
        \[ x > \frac{ 1 }{ \epsilon  } \iff \frac{ 1 }{ x } < \epsilon. \]
        Hence, we have that 
        \[  | f(x) - 0  | < \epsilon. \]
        This means \( \lim_{ x \to \infty  } f(x) = 0  \).
        \end{proof}
\end{enumerate}


\subsubsection{Exercise 4.2.11(Squeeze Theorem).} Let \( f,g, \) and \( h \) satisfy \( f(x) \leq g(x) \leq h(x) \) for all \( x  \) in some common domain \( A  \). Suppose \( f(x) \leq g(x) \leq h(x) \ \). If \( \lim_{ x \to c  } f(x) = L  \) and \( \lim_{ x \to c } h(x) = L  \) at some limit point \( c \) of \( A  \), show 
\[  \lim_{ x \to c } g(x) = L  \] as well.
\begin{proof}
Let \( (x_n), (y_n), (z_n) \subseteq A   \). Suppose \( \lim_{ x \to c } f(x) = L  \) and \( \lim_{ x \to c } h(x) = L  \) at some limit point \( c \) of \( A  \). Using the Sequential Criterion for Functional Limits, let \( f(x_n) \to L  \) and \( h(z_n) \to L  \). There exists \( N \in \N  \) such that for any \( n \geq N  \), we have 
\[ f(x_n) \leq g(y_n) \leq h(z_n) \iff L \leq g(y_n) \leq L. \]
Hence, we have \( g(y_n) \to L  \) by the Squeeze Theorem for Sequences. By the Sequential Criterion, we must have \( \lim_{ x \to c } g(x) = L  \) as well.
\end{proof}




