
\section{Compact Sets}

\subsection{Compactness}
\begin{tcolorbox}
\begin{defn}
A set \( K \subseteq \R \) is compact if every sequence in \( K \) has a subsequence that converges to a limit that is also in \( K \).
\end{defn}
\end{tcolorbox}

\begin{ex}
\begin{enumerate}
    \item[(i)] Closed intervals are compact since all \( (a_n) \) in \( K \) are bounded and so we can always find a subsequence in \( K \) (By Bolzano-Weierstrass) that converges to a limit that is contained within the closed interval. We know the limit is contained in \( K \) since closed intervals are closed sets. 
\end{enumerate}
\end{ex}

In the example above, we used the fact that bounded sequences contain subsequences that converge and the fact that their limits are contained since closed intervals are closed sets. 

\begin{tcolorbox}
\begin{defn}
A set \( A \subseteq \R \) is \textit{bounded} if there exists \( M > 0  \) such that \( | a | \leq M  \) for all \( a \in A \).
\end{defn}
\end{tcolorbox}

\begin{tcolorbox}
    \begin{thm}[Characterization of Compactness in \( \R \)]
    A set \( K \subseteq \R \) is compact if and only if it is closed and bounded.
    \end{thm}
\end{tcolorbox}

\begin{proof}
    Assume \( K \) is a compact set. Suppose for sake of contradiction that \( K \) is not a bounded set. Our goal is to construct a sequence \( (a_n) \) that diverges. Since \( K \) is not bounded, for all \( M > 0  \), there exists \( a_n \in A \) such that \( | a_n | > M  \). But by assumption, \( K \) is compact so \( (a_n) \) must contain a subsequence \( (a_{n_k}) \) that converges to a limit in \( K \). But since \( (a_{n_k}) \) is unbounded, we have a contradiction. Hence, \( K \) must be a bounded set. 

    Now we will show that \( K \) is closed. Since \( K \) has to be bounded, then \( (a_n) \subseteq K  \) must contain a subsequence \( (a_{n_k}) \) that converges to a limit in \( K \). But this is the definition of a closed set. Hence, \( K \) is a closed set.

    Assume that \( K \) is closed and bounded. Let \( (a_n) \) be an arbitrary sequence in \( K \). Since \( K  \) is bounded and hence \( (a_n) \) is bounded, \( (a_n) \) contains a subsequence \( (a_{n_k}) \) such that \( (a_{n_k}) \to a  \). Since \( K  \) is closed, \( a  \) is contained in \( K \). Hence, we have that \( K \) is a compact set.
\end{proof}

It is important remember that closed intervals are not all that is when considering compact sets. The structure is much more intricate and interesting. For example, we can say that the Cantor Set is compact. We can experiment with this new idea of compact sets with the Nested Interval Property from chapter 1.


\begin{tcolorbox}
    \begin{thm}[Nested Compact Set Property]
    If 
    \[ K_1 \supseteq K_2 \supseteq K_3 \supseteq K_4 \supseteq \dots \]
    is a nested sequence of nonempty compact sets, then the intersection \( \bigcap_{ n=1 }^{ \infty  } K_n  \) is not empty.
    \end{thm}
\end{tcolorbox}

\begin{proof}
    Assume \( K_n \neq \emptyset  \) compact for each \( n \in \N \). Then for each \(  n \in \N \), choose \( x_n \in K_n \) where \( x_n \) is a sequence of points. Since we have a nested sequence of nonempty sets, it follows that \( x_n \in K_1 \). By definition of compactness, \( (x_n) \) contains a convergent subsequence \( (x_{n_k}) \) such that \( \lim x_{n_k} = x  \) where \( x \in K_n \) for every \( n \in \N \) and thus \( x \in K_1 \). Given \( n_0 \in \N \), we have that the terms of the sequence \( x_n  \) are contained within \( K_{n_0} \) given all \( n \geq n_0 \). We can ignore the finite number of terms for which \( n_k < n_0  \) so that \( (x_{n_k}) \) can be contained in \( K_{n_0} \). Hence, we have that \( x = \lim x_{n_k} \) is an element of \( K_{n_0} \). Because \( n_0  \) was arbitrary, we have that \( x \in \bigcap_{ n=1 }^{ \infty  } K_n \neq \emptyset\).
\end{proof}

\subsection{Open Covers}
In the last section, we proved that compact sets to be bounded and closed and vice versa. In other cases, we could also have defined compacts in this way and then proved that for every sequences that is bounded, there exists subsequences that converge to limits contained within the set. We can prove compactness in terms of open covers and finite subcovers. 

\begin{tcolorbox}
\begin{defn}
    Let \( A \subseteq \R \). An \textit{open cover} for \( A \) is a (possibly infinite) collection of open sets \( \{ O_{\lambda} : \lambda \in \Lambda \}  \) whose union contains the set \( A \); that is 
    \[ A \subseteq \bigcup_{ \lambda \in \Lambda } O_{\lambda}.  \]
    Given an open cover for \( A \), a \textit{finite subcover} is a finite subcollection of open sets from the original open cover whose union still manages to completely contain \( A \).
\end{defn}
\end{tcolorbox}

Subcollection in this context is just a collection of sets that are subsets of the original collection of open sets.

\begin{ex}
Consider the open interval \( (0,1) \). For each point \( x \in (0,1) \), let \( O_x \) be the open interval \( (x/2, 1) \). Let the infinite collection of \( O_x \) be defined as 
\[ \{ O_{x} : x \in (0,1) \}  \]
forms an open cover for the open interval \( (0,1) \); that is, 
\[  (0,1) \subseteq \bigcup_{ x \in (0,1) } O_x.  \]
Note that it is impossible to find a finite subcover for the open set \( (0,1) \). Given any proposed finite subcollection 
\[ \{ O_{x_1}, O_{x_2}, ..., O_{x_n} \}, \]
let \( x' = \min \{ x_1, x_2, \dots, x_n \}  \) and observe that for any \( y \in \R  \) satisfying \( 0 < y \leq x' /2  \) is not contained in the union \( \bigcup_{ i=1 }^{ n } O_{x_i} \). 
\end{ex}

Now consider a similar cover for the closed interval \( [0,1] \). For \( x \in (0,1) \), the sets \( O_x = (x/2, 1) \) do relatively well to cover \( (0,1) \), but in order to have an open cover for the closed interval \( [0,1] \), we could let \( \epsilon > 0   \) so that we can have epsilon neighborhoods covering both endpoints. That is, we have \( O_o = (-\epsilon , \epsilon ) \) and \( O_1 = (1 - \epsilon, 1 + \epsilon ) \). Then the collection 
\[ \{ O_0, O_1, O_x : x \in (0,1) \}  \]
is an open cover for \( [0,1] \) is a finite subcover for the closed interval \( [0,1] \).

\begin{tcolorbox}
    \begin{thm}[Heine-Borel Theorem]
Let \( K \) be a subset of \( \R \). All of the following statements are equivalent in the sense that any one of them implies the two others. 
\begin{enumerate}
    \item[(i)] \( K \) is compact.
    \item[(ii)] \( K \) is closed and bounded.
    \item[(iii)] Every open cover for \( K \) has a finite subcover.
\end{enumerate}
\end{thm}
\end{tcolorbox}

\begin{proof}
Notice that the proof of the equivalence of (i) and (ii) has already been proven in Theorem 3.3.1. All we need to show now is that (iii) implies (ii) and (iii) implies (i). 

To show (ii), we must show that \( K \) is both bounded and closed. To show that \( K \) is bounded, let us construct an open cover for \( K \) by defining \( O_x  \) to be an open interval of radius \( 1 \) (\( \epsilon  = 1  \)) for each \( x \in K \). This means there exists a \( \epsilon - \)neighborhood for each \( x \in K \); that is, \( O_x = V_1(x) \). Since the open cover \( \{ O_x : x \in K \}  \) contains a finite subcover for \( K \), we have the \( K \) contained in the union of the collection of sets \( \{ O_{x_1}, O_{x_2}, \dots , O_{x_n} \}  \). Hence, \( K \) itself is a bounded set.

Now let us show that \( K \) is closed. Let \( (y_n) \) be a Cauchy sequence contained in \( K \) with \( \lim y_n = y  \). To show that \( K \) is closed, we must show that \( y \in K \). Suppose for sake of contradiction that \( y \notin K  \). By assumption we can construct an open cover by taking \( O_x  \) to be an interval of radius \( | x - y  | / 2  \) around each point \( x \in K \). Also, we are assuming that the open cover \( \{ O_x : x \in K \}  \) for \( K \) contains a finite subcover \( \{ O_{x_1}, O_{x_2}, \dots, O_{x_n} \}  \). If \( y \notin K \), then the distance from \( y \) to each \( x_i \in K \) must be 
\[ \epsilon_0 := \min \Big\{ \frac{ | x_i - y  |  }{ 2  }   : 1 \leq i \leq n \Big\}.\]
Since \( (y_n) \) is a Cauchy sequence, so it must converge. Hence, for some \( N \in \N \), we know that 
\[ | y_N - y  | < \epsilon_0 \] we must have for every \( n \geq N \), 
But note that since \( y \notin K  \), not all of the terms from the sequence \( (y_n) \) for every \( n \geq N \) that is contained in \( K \) are not included in the finite subcover
\[ \bigcup_{ i=1 }^{ n } O_{x_i}. \]
Hence, our finite subcover does not actually cover all of \( K \) which is a contradiction and thus we must have \( y \in K \).




\end{proof}



\subsection{Exercises}

\subsubsection{Exercises 3.3.1} Show that if \( K \) is compact and nonempty, then \( \sup K  \) and \( \inf K \) both exists and are contained in \( K \).
\begin{proof}
   Suppose \( K \) is compact. By the equivalence theorem, \( K \) is bounded. Since \( K \) is nonempty and bounded above and below, \( \sup K  \) exists and \( \inf K \) exists by the Axiom of Completeness. We begin by constructing a sequence \( (x_n) \) that is contained in \( K \) such that we want to show that \( (x_n) \to \sup K \). Let \( \epsilon > 0  \). Since \( \sup K \) is the least upper bound, we can have \( \sup K - \epsilon   \) be not an upper bound. But since \( (x_n) \subseteq K \), we must have \( x_n \leq \sup K \). Together we have 
\[ \sup K - \epsilon \leq x_n \leq \sup K. \]
Since \( \epsilon > 0  \) is arbitrary, the sequence \( (x_n) \to \sup K \). Since \( K  \) is closed \( \sup K \) must be contained in \( K \). By a similar reasoning, we can generate \( (x_n) \)
so that \( (x_n) \to \inf K \) which is also contained in \( K \). Hence, \( \sup K  \) and \( \inf K \) contained in \( K \).
\end{proof}

\subsubsection{Exercise 3.3.2} Decide which of the following sets are compact. For those that are not compact, show how Definition 3.3.1 breaks down. In other words, give an example of a sequence contained in the given set that does not possess a subsequence converging to a limit in the set.

\begin{enumerate}
    \item[(a)] \( \N \).
        \begin{proof}[Solution]
        Not compact. We can see that for every \( n \in \N \), the sequence \( a_n = n  \) diverges to infinity and so does its subsequences; that is, if we define the odd and even subsequences \( (a_n) \) where both sequences also converge to infinity.
        \end{proof}
    \item[(b)] \( \Q \cap [0,1] \).
        \begin{proof}[Solution]
        This set is compact because it is bounded and closed.
        \end{proof}
    \item[(c)] The Cantor set.
    \begin{proof}[Solution]
    The cantor set is closed.
    \end{proof}
\item[(d)] \( \{ 1 + 1/2^2 + 1/3^2 + \dots + 1/n^2 : n \in \N \}.  \)
    \begin{proof}[Solution]
    This set is not compact since the limit point of this set (\( L = \{ 0 \}  \)) is not contained in the set.
    \end{proof}
\item[(e)] \( \{ 1, 1/2, 2/3, 3/4, 4/5, \dots \}.  \)
    \begin{proof}[Solution]
        This set is compact since its limit point \( L = \{ 1 \}  \) is contained in the set and the fact that it is bounded by \( 1 \) and \( 0 \). 
    \end{proof}
\end{enumerate}


\subsubsection{Exercise 3.3.3} Prove the converse of Theorem 3.3.4 by showing that if a set \( K \subseteq \R \) is closed and bounded, then it is compact.

\begin{proof}
    Assume that \( K \) is closed and bounded. Our goal is to show that \( K \) is compact. Let \( (a_n) \) be a sequence contained in \( K \). Since \( K  \) is bounded, we know that \( (a_n) \) is also bounded. Hence, there exists a subsequence \( (a_{n_k}) \) such that \( (a_{n_k}) \to a \). But since \( K \) is closed and \( a \) is a limit point of \( K \), we have that \( \lim a_{n_k} = a  \) is also contained in \( K \).
\end{proof}

\subsubsection{Exercise 3.3.4} Assume \( K  \) is compact and \( F \) is closed. Decide if the following sets are definitely compact, definitely closed, both or neither.

\begin{enumerate}
    \item[(a)] \( K \cap F \).
        \begin{proof}[Solution]
            Compact.
        \end{proof}
    \item[(b)] \( \overline{F^c \cup K^c} \).
        \begin{proof}[Solution]
            Closed.
        \end{proof}
    \item[(c)] \( K \setminus F = \{ x \in K : x \notin F \}  \)
        \begin{proof}[Solution]
        Definitely compact.
        \end{proof}
    \item[(d)] \( \overline{K \cap F^c} \).
        \begin{proof}[Solution]
        Definitely compact.
        \end{proof}
\end{enumerate}

\subsubsection{Exercise 3.3.8} Let \( K  \) and \( L  \) be nonempty compact sets, and define 
\[ d = \inf \{ | x - y  | : x \in K ~ \text{and} ~ y \in L \}.  \]
This turns out to a reasonable definition between \( K \) and \( L \). 
\begin{enumerate}
    \item[(a)] If \( K  \) and \( L \) are disjoint, show \( d > 0  \) and that \( d = | x_0 - y_0 |  \) for some \( x_0 \in K \) and \( y_0 \in L \).
        \begin{proof}
        Suppose \( K \) and \( L \) are disjoint, nonempty compact sets. Our goal is to show that \( d > 0  \) and that \( d = | x_0 - y_0  |  \) for some \( x_0 \in K  \) and \( y_0 \in L \). Since \( K \) and \( L \) are nonempty compact sets, we also have that \( K \) and \( L \) are bounded sets. Hence, \( \inf A \) exists where 
        \[ A = \{ | x - y | : x \in K ~ \text{and} ~ y \in L \}  \]
by the Axiom of Completeness. Then by lemma 1.3.8, we have that for some \( x_0 \in K \) and \( y_0 \in L \), consider the distance \( d = | x_0 - y_0  | \in A   \) such that we have
\[ d = | x_0 - y_0  | > \inf A + \epsilon  \]
for all \( \epsilon > 0  \). Since \( K \) and \( L \) are disjoint and \( \epsilon > 0  \) is arbitrary, we have \(d =  |x_0 - y_0  | > 0  \). Hence, we have that \( d > 0  \).
        \end{proof}
        Technically, the proof above is not valid yet since we haven't gone over functions and how compactness imply continuity.
        \begin{proof}
            Suppose \( K \) and \( L \) are non-empty compact sets that are disjoint. Suppose for sake of contradiction that \( d = 0  \). Since \( K \) and \( L \) are both compact, let \( (x_n) \) and \( (y_n) \) contain subsequences \( (x_{n_k}) \) and \( (y_{n_k}) \) that converge to \( x_0  \) and \( y_0 \) respectively. We want to show that \( \lim | x_{n_k} - y_{n_k} | = | x_0 - y_0 |  \). Let \( \epsilon > 0  \). Then for every \( n_k > N  \) for some \( N \in \N \), we have that 
            \begin{align*}
                | | x_{n_k} - y_{n_k}| - | x_0 - y_0 |   | &\leq | (x_{n_k} - y_{n_k}) - (x_0 - y_0) |  \\
                                                           &= | (x_{n_k} - x_0) + (y_0- y_{n_k}) |  \\
                                                           &\leq | x_{n_k} - x_0 | + | y_{n_k} - y_0  | \\   
                                                           &< \frac{ \epsilon  }{ 2 }  + \frac{ \epsilon  }{ 2 }  \\
                                                           &= \epsilon.
            \end{align*}
            Since \( d = | x_0 - y_0 | = 0   \), we have that \( \lim | x_{n_k} - y_{n_k} | = d = 0   \). But this means that \( K \cap L \neq \emptyset \) since \( K \) and \( L \) are closed sets which is a contradiction. Hence, we must have \( d > 0  \).
        \end{proof}
    \item[(b)] Show that it's possible to have \( d = 0  \) if we assume only that the disjoint sets \( K \) and \( L \) are closed.
        \begin{proof}
            Basically the argument above but taking away the fact that \( K \) and \(  L \) are compact sets.
        \end{proof}
\end{enumerate}

\subsubsection{Exercise 3.3.9} Follow these steps to prove the final implication in Theorem 3.3.8. 
Assume \( K \) satisfies (i) and (ii), and let \( \{ O_{\lambda} : \lambda \in \Lambda  \}  \) be an open cover for \( K \). For contradiction, let's assume that no finite subcover exists. Let \( I_0  \) be a closed interval containing \( K \).
\begin{enumerate}
    \item[(a)] Show that there exists a nested sequence of closed intervals \( I_0 \supseteq I_1 \supseteq I_2 \supseteq \dots \) with the property that, for each \( n  \), \( I_n \cap K \) cannot be finitely covered and \( \lim | I_n | = 0  \).
        \begin{proof}
        Let \( I_1  \) be a half of \( I_0 \) whose intersection with \( K \) does not have a finite subcover, so that \( I_1 \cap K \) cannot be finitely covered and \( I_1 \subseteq I_0  \). Then bisect \( I_1  \) into two closed intervals \( A_2 \) and \( B_2 \), and again let \( A_2 = I_2  \) such that \( A_2 \cap K  \) does not have a finite subcover. Otherwise, \( B_2 = I_2  \) such that \( B_2 \cap K \) does not contain a finite subcover. Hence, \( I_2 \subseteq I_1 \subseteq I_0 \). We can repeat this process of bisecting each interval \( I_n  \) and determining which closed set does not have a finite subcovers until we have our desired sequence \( I_n \) such that \( \lim I_n = 0 \).
    \end{proof}
    \item[(b)] Argue that there exists an \( x \in K \) such that \( x \in I_n \) for all \( n \).
        \begin{proof}
        Since \( K \) is compact, \( K \cap I_n \) is also compact for each \( n \in \N \). Hence, we know that \( \bigcap_{ n=1 }^{ \infty  } I_n \cap K \) is non-empty, and there exists \( x \in K \cap I_n \) for all \( n \).
        \end{proof}
    \item[(c)] Because \( x \in K \), there must exists an open set \( O_{\lambda_0} \) from the original collection that contains \( x  \) as an element. Explain how this leads to the desired contradiction.
\begin{proof}
    Let \( x \in K \) and let \( O_{\lambda_0} \) be an open set that contains \( x \). Since \( O_{\lambda_0} \) is an open set, we can construct an \( \epsilon - \)neighborhood such that \( V_{\epsilon_0 }(x) \subseteq O_{\lambda_0} \). Now choose \( n_0  \) such that for every \( n \geq n_0 \), \( | I_{n_0}| < \epsilon_0  \). Hence, \( I_{n_0} \) is contained within a single open set \( O_{\lambda_0} \) which means it has a finite subcover. This contradiction tells us that \( K \) must have had a finite subcover.
\end{proof}
\end{enumerate}

\subsubsection{Exercise 3.3.10} Here is an alternate proof to the one given in Exercise 3.3.9 for the final implication in the Heine-Borel Theorem. Consider the special case where \( K \) is a closed interval. Let \( \{ O_{\lambda} : \lambda \in \Lambda\}  \) be an open cover for \( [a,b] \) and define \( S \) to be the set of all \( x \in [a,b] \) such that \( [a,x] \) has a finite subcover from \( \{ O_{\lambda} : \lambda \in \Lambda \}  \).
\begin{enumerate}
    \item[(a)] Argue that \( S \) is nonempty and bounded, and thus \( s = \sup S \) exists.
        \begin{proof}
            Let \( S \) be defined as the set of all \( x \in [a,b] \) such that \( [a,x] \) has a finite subcover from \( \{ O_{\lambda} : \lambda \in \Lambda \}  \). Since \( [a,b] \) is a closed interval, we can define a sequence of points \( (x_n) \) that converges to \( x \in [a,b] \). Since \( \{ O_{\lambda} : \lambda \in \Lambda\}  \) is an open cover for \( [a,b] \), we know that there must exists a finite cover for \( [a,x] \). Hence, \( S \) is nonempty and \( S \) is bounded since \( a \leq x \leq b \). By the Axiom of Completeness, \( s = \sup S \) exists.
        \end{proof}
    \item[(b)] Now show \( s = b  \), which implies \( [a,b] \) has a finite subcover. 
        \begin{proof}
            Since \( [a,b] \) is a closed and bounded interval, it follows that \( [a,b] \) is a compact set. By exercise 3.3.1, \( [a,b] \) must contain its supremum. Hence, \( \sup [a,b] \in S \) and hence, \( [a,b] \) must have a finite subcover.
        \end{proof}
    \item[(c)] Finally, prove the theorem for an arbitrary closed and bounded set \( K \).
        \begin{proof}
            Let \( K \) be a closed and bounded set. From (a) and (b), \( K \) must have finite subcover from \( \{ O_{\lambda} : \lambda \in \Lambda \}  \).
        \end{proof}
\end{enumerate}

Other solutions (not mine).

\begin{enumerate}
    \item[(b)] Now show \( s = b  \), which implies \( [a,b] \) has a finite subcover.
        \begin{proof}
            Suppose for contradiction that \( s < b  \), letting \( s \in O_{\lambda_0} \) implies \( [a,s] \) is finitely coverable since we can take the finite cover of an \( x \in O_{\lambda_0} \) with \( x < s  \). This causes a contradiction however since there exists points \( y > s  \) with \( y \in O_{\lambda_0} \) meaning \( [a,y] \) is also finitely coverable. Therefore, the only option is \( s = b  \), since any \( s < b  \) fails.
    \end{proof}
\item[(c)] We must also consider the case where \( y \) does not exists; that is, there exists a "gap". Let \(  y = [s,b] \cap K  \) and suppose \( y \neq s  \). Since \(  y \in [s,b] \cap K \) we know 
    \[ [a,y] \cap K = ([a,s] \cap K ) \cup ([s,y] \cap K) = [a,s] \cap K \cup {y}. \]
    Therefore if \( \{ O_{\lambda_1}, \dots, O_{\lambda_{n}} \}  \) covered \( [a,s] \) then letting \( y \in O_{\lambda_{n+1}} \) would give the finite cover \( \{ O_{\lambda_1}, \dots, O_{\lambda_{n+1}}\}  \) contradicting the assumption that \( s < b  \), therefore \( s = b  \) is the only option, and so \( K \) can be finitely covered.
\end{enumerate}




