
% !TEX root =  ../../../main.tex 


\section{Double Summations and Products}

We discovered in an earlier section that given any doubly indexed array of real numbers \( \{  a_{ij} : i,j \in \N  \}\), it can be an ambiguous task to define 
\[ \sum_{i,j = 1}^{\infty} a_{ij}. \tag{1}\]
We also observed that performing \textit{iterated summations}can lead to different summations. Of course, this can be avoided completely if we were to define the partial sum of (1) in the following way 
\[ s_{mn} =  \sum_{i=1}^{m} \sum_{j=1}^{n} a_{ij}\]
for \( m, n \in \N \). In order for the sum of (1) to converge we have to have the following hold:
\[ \sum_{i,j = 1 }^{\infty} a_{ij} = \lim_{n \to \infty} s_{mn}\]

\subsubsection{Exercise 2.8.1} Using the particular array \( (a_{ij})\) from Section 2.1, compute \( \lim_{n \to \infty} s_{mn}\). How does this value compare to the two iterated values for the sum already computed?  

The double summation from section 2.1 is \( a_{ij} = \frac{1}{2^{j-i}}\) where \( \{ a_{ij} : i, j \in \N  \}\) if \( j > i \), \( a_{ij} = -1 \) if \( j = i \), and \( a_{ij} = 0 \) if \( j < i \). 
\begin{proof}
    To find \( \sum_{i,j = 1}^{\infty} a_{ij} = \lim_{n \to \infty} s_{mn}\), we first need to define the sequence of partial sums. We can fix \( j \) (the rows of the matrix) and define the sequence of partial sums for the series \( \sum_{i,j = 1 }^{\infty} a_{ij}\) as 
    \[ s_n = \sum_{k=1}^{n} \Big( \frac{1}{2^{n-1}}\Big) = -2 + \frac{1}{2^{n-1}} \]
    which taking the limit leads to 
    \[ \lim_{n \to \infty} \Big( -2 + \frac{1}{2^{n-1}} \Big) = -2.\]

\end{proof}

The issue of rearrangements to an infinite series arises due to commutativity of addition in an infinite context. It was found that having an absolutely converging infinite series fixes this problem. 

\subsubsection{Exercise 2.8.2}

Show that if the iterated series 
\[ \sum_{i=1}^{\infty} \sum_{j=1}^{\infty} |a_{ij}|\]
converges (meaning that for each fixed \( i \in \N \) the series \( \sum_{j=1}^{\infty} |a_{ij}|\) converges to some \( b_i \in \R \), and the series \( \sum_{i=1}^{\infty} b_i \) converges as well), then the iterated series 
\[ \sum_{i=1}^{\infty} \sum_{j=1}^{\infty} a_{ij}\]
converges.

\begin{proof}
Suppose the iterated series 
\[ \sum_{i=1}^{\infty} \sum_{j=1}^{\infty} |a_{ij}|  \tag{1}\]
converges. This means that the (1) meets the \textit{Cauchy Criterion}. Let \(\epsilon > 0 \). This implies that there exists \( N \in \N \) such that for every \( n > m  \geq N \), we have that 
\[ \sum_{i= p + 1}^{m} \sum_{j= \ell + 1}^{n} |a_{ij}| < \epsilon.\]
Consider \( \Big| \sum_{i=p+1}^{\infty} \sum_{j = \ell + 1 }^{\infty} a_{ij} \Big|\). Using the \textit{Triangle Inequality}, we find that  
j\begin{align*}
    \Big| \sum_{i=p+1}^{\infty} \sum_{j = \ell + 1 }^{\infty} a_{ij} \Big|&\leq \sum_{i=p+1}^{\infty} \Big|\sum_{ j = \ell + 1 }^{\infty} a_{ij} \Big|   \\
                                                                          &\leq \sum_{i = p + 1}^{\infty} \sum_{j = \ell + 1 }^{\infty} |a_{ij}| \\
                                                                          &< \epsilon.
\end{align*}
Since (1) meets the \textit{Cauchy Criterion} for series, we know that (1) converges as well. 
\end{proof}

Another proof using the Comparison Test goes something like this

\begin{proof}
    Suppose the iterated series 
    \[ \sum_{i=1}^{\infty} \sum_{j=1}^{\infty} |a_{ij}| \]
    converges. This means that for each \( i \in \N \) the infinite series 
    \[ \sum_{j=1}^{\infty} a_{ij} = r_i \] for some \( r_i \in \R \). Hence, we have the infinite series 
    \[ \sum_{i=1}^{\infty} r_i. \tag{1} \]
    Our goal is to show that (1) converges. Suppose we look at the terms 
    \[ |r_i| = \Big| \sum_{j=1}^{\infty} a_{ij}\Big|.\]
    Note by the \textit{Triangle Inequality} that 
    \[ \sum_{i=1}^{\infty} |r_i| \leq \sum_{i=1}^{\infty} \sum_{j=1}^{\infty} |a_{ij}|.  \]
    by assumption the infinite series to the right converges. Hence, the series to the left must also converge by the \textit{Comparison Test}. Since \( \sum |r_i|\) converges, then the series 
    \( \sum r_i \) converges by the \textit{ Absolute Convergence Test }. 
\end{proof}

\begin{tcolorbox}
\begin{thm}
    Let \( \{ a_{ij} : i,j \in \N  \}\) be a doubly indexed array of real numbers. If 
    \[ \sum_{i=1}^{\infty} \sum_{j=1}^{\infty} |a_{ij}|\]
    converges, then both \( \sum_{i=1}^{\infty} \sum_{ j=1 }^{ \infty  }  a_{ij}\) and \( \sum_{j=1}^{\infty} \sum_{i=1}^{\infty} a_{ij} \) converge to the same value. Moreover, we have that 
    \[ \lim_{n \to \infty} s_{nn} = \sum_{i=1}^{\infty} \sum_{j=1}^{\infty} a_{ij} = \sum_{i=1}^{\infty} \sum_{j=1}^{\infty} a_{ij},\]
    where \( s_{nn} = \sum_{i=1}^{n} \sum_{j=1}^{n} a_{ij}\). 
\end{thm}
\end{tcolorbox}

\begin{proof}
    In the same way that we defined the rectangular partial sums \( s_{mn}\) above in equation (1)
    , define 
    \[ t_{mn} =  \sum_{ i=1 }^{ m } \sum_{ j=1 }^{ n }  | a_{ij} |.\] 

\end{proof}

\subsubsection{Exercise 2.8.3}

\begin{enumerate}
    \item[(a)] Prove that \( (t_{nn})\) converges. 
        \begin{proof}
            From our definition of \( t_{nn}\) above we have 
            \[ t_{nn} = \sum_{ i=1 }^{ n } \sum_{ j=1 }^{ n } | a_{ij} |.\] 
            We want to show for all \(\epsilon > 0 \), there exists \( N \in \N \) such that for all \( n \geq  N \), we have that  \( |t_{nn} - L  | < \epsilon \). By assumption, we know that 
            \[  \sum_{ i=1 }^{ \infty  } \sum_{ j=1 }^{ \infty  } | a_{ij} |  \tag{1}\] 
            converges absolutely which implies that 
            \[  \sum_{ i=1 }^{ \infty  } \sum_{ j=1 }^{ \infty   } a_{ij} \] 
            converges. Note that \( t_{nn} = \sum_{ i=1 }^{ \infty   } \sum_{ j=1 }^{ \infty  } a_{ij}  \to s_n = \sum_{ i=1 }^{ \infty  } r_i \) for some \( r_i \in \R  \). Furthermore, we have \( s_n \to L  \) since (1) converges. Let \( \epsilon  > 0  \). Then there exists \(  N \in \N  \) such that for any \(  n \geq N  \), we have that 
            \begin{align*}
                | t_{nn} - L  | &= | t_{nn} -s_n + s_n - L |  \\
                                &\leq  | t_{nn} - s_n  | + | s_n - L  | \\
                                &< \frac{ \epsilon  }{ 2 } + \frac{ \epsilon  }{ 2 } \\
                                &= \epsilon.
            \end{align*}
            Hence, the sequence of partial sums \(  (t_{nn}) \) converges. 
        \end{proof}
    \item[(b)] Now, use the fact that \( (t_{nn})\) is a Cauchy sequence to argue that \( (s_{nn})\) converges. In order to prove the theorem, we must show that the two iterated sums converge to this same limit. We will first show that 
        \[ S = \sum_{ i=1 }^{ \infty  } \sum_{ j=1 }^{ \infty  } a_{ij}, \] 
        Because \( \{ t_{mn} : m,n \in \N  \} \) is bounded above, we can let 
        \[ B = \sup \{ t_{mn}: m,n \in \N  \}.\] 
        \begin{proof}
        Suppose \( (t_{nn}) \) is a Cauchy Sequence. Then for some \( N \in \N \) we have that for any \( n \geq m > N  \)
        \[  | t_{nn} - t_{mm} | < \epsilon.  \]
        We can rewrite this in the following way to say that 
        \[  | \sum_{ n,m } t_{ij} | < \epsilon.    \]
        Our goal is to show that 
        \[  | s_{nn} - s_{mm} | < \epsilon.   \]
        Hence, for any \( n \geq  m > N  \), we have that 
        \begin{align*}
            | s_{nn} - s_{mm } | &\leq | t_{nn} - t_{m m }|  \\
                                 &= \Big| \sum_{ n,m } t_{ij} \Big|  \\
                                 &< \epsilon.
        \end{align*}
        Hence, \( (s_{nn}) \) converges.

        \end{proof}

    Now, use the fact that \( (t_{nn})\) is a Cauchy sequence to argue that \( (s_{nn})\) converges. In order to prove the theorem, we must show that the two iterated sums converge to this same limit. We will first show that 
        \[ S = \sum_{ i=1 }^{ \infty  } \sum_{ j=1 }^{ \infty  } a_{ij}, \] 
        Because \( \{ t_{mn} : m,n \in \N  \} \) is bounded above, we can let 
        \[ B = \sup \{ t_{mn}: m,n \in \N  \}.\] 
        \subsubsection{Exercise 2.8.4}     
        \begin{enumerate}
            \item[(a)] Let \( \epsilon > 0  \) be arbitrary and argue that there exists an \(  N_1 \in \N  \) such that \( m,n \geq  N_1 \) implies \( B - \frac{ \epsilon  }{ 2 } < t_{mn} \leq  B.\)
                \begin{proof}
                    Since \( (t_{mn}) \) bounded, we can say that \( t_{mn} \leq B \). Since the set 
                    \[  \{ t_{mn} : m,n \in \N \}  \]
                    is bounded above and non-empty, we also have that 
                    \( B = \sup \{ t_{mn}: m,n \in \N  \}  \) exists. Hence, for any \( \epsilon > 0  \), we have that \( B - \frac{ \epsilon  }{ 2 }  \) is not an upper bound. Hence, there exists some \( t_{n_0 m_0} \) such that \( B - \frac{ \epsilon  }{ 2 } < t_{m_0 n_0} \leq t_{mn}\). Furthermore, there exists \( N_1 \in \N  \) such that for any \(  n \geq m > N_1  \) since \( (t_{mn}) \) converges. Hence,  we must have that 
                    \( B - \frac{ \epsilon  }{ 2 } < t_{mn} \leq B \)
                \end{proof}
            \item[(b)] Now, show that there exists an \( N  \) such that 
            \[ | s_{mn} - S  | < \epsilon \]
            for all \( m,n \geq N \).
            \begin{proof}
                Consider \(  | s_{mn} - S  | < \epsilon \). Since \(  (s_{nn}) \to S  \), let \( \epsilon > 0  \) such that for some \( N_2 \in \N  \) we have \( n \geq m > N_2  \), we have
                \[ | s_{nn} - S  | < \frac{ \epsilon  }{ 2 } . \]
                Since \( (s_{nn}) \) meets the Cauchy Criterion, we have that there exists \( N_2 \in \N  \) such that for any \( n \geq m > N  \), we have 
                \[ | s_{nn} - s_{mn} | < \frac{ \epsilon  }{ 2 }.   \]
                Hence, observe that for any \( n \geq m > N = \max \{ N_1, N_2 \}  \), we have
                \begin{align*}
                    | s_{mn} - S  | &= | s_{mn} - s_{nn} + s_{nn} - S  |  \\
                                    &\leq  | s_{mn} - s_{nn} | + | s_{nn} - S  | \\ 
                                    &< \frac{ \epsilon  }{ 2 } + \frac{ \epsilon  }{ 2 } \\
                                    &= \epsilon.
                \end{align*}
                Hence, we have that \( (s_{mn} ) \to S \). 
            \end{proof}
        \end{enumerate}

        Our hypothesis guarantees that for each fixed row \( i \), the series \( \sum_{ j=1 }^{ \infty  } a_{ij} \) converges absolutely to some real number \( r_i  \). 

        \subsubsection{Exercise 2.8.5}
        \begin{enumerate}
            \item[(a)] Show that for all \( m \geq N \) 
                \[ | (r_1 + r_2 + ... + r_m) - S  | \leq \epsilon. \]
                Conclude that the iterated sum \( \sum_{ i=1 }^{ \infty  } \sum_{ j=1 }^{ \infty  } a_{ij} \) converges to \( S \). 
        \end{enumerate}

\end{enumerate}






