\documentclass[a4paper]{report}
\usepackage{standalone}
\usepackage{import}
\input{../../../../../newpreamble.tex}

\begin{document}

\subsection{Topics}

\begin{enumerate}
    \item[(1)] Every neigborhood is an open set.
    \item[(2)] If \( p  \) is a limit point of a set \( E  \), then every neighborhood of \( p  \) contains infinitely many points of \( E  \). 
    \item[(3)] Theorem: \( E  \) is open \( \Longleftrightarrow \) \( E^{C}   \) is closed.
    \item[(4)] Theorem: arbitrary union of open sets is open, Finite intersection of open sets is open.
    \item[(5)] Theorem: \( \overline{E} \) is the smallest closed subset of \( X  \) that contains \( E  \).
\end{enumerate}

\begin{theorem}[ ]
   Let \( (X,d) \) be a metric space and let \( p \in X  \) and \( \epsilon > 0  \). Every neighborhood is an open set; that is, \( {N}_{\epsilon}(p) \) is an open set.
\end{theorem}

\begin{proof}
Our goal is to show that every point of \( {N}_{\epsilon}(p) \) is an interior point of \( {N}_{\epsilon}(p) \). Let \( q \in {N}_{\epsilon}(p) \). We need to show that there exists \( \delta > 0  \) such that \( {N}_{\delta}(q) \subseteq {N}_{\epsilon}(p) \). Let \( \delta = \frac{ \epsilon - d(p,q)  }{ 2 }  \). We claim that \( {N}_{\delta}(q) \) is a subset of \( {N}_{\epsilon}(p) \). Indeed, if \( x \in {N}_{\delta}(q) \), then  
\[  d(q,x) < \delta \Longrightarrow d(q,x) < \epsilon - d(p,q)  \]
and so
\[  d(p,q) + d(q,x) < \epsilon \Longleftrightarrow d(p,x) < \epsilon \tag{triangle inequality}. \]
Thus, \( x \in {N}_{\epsilon}(p) \).

\end{proof}

\begin{theorem}[ ]
    Let \( (X,d) \) be a metric space and \( E \subseteq X  \). If \( p \in E' \), then every neighborhood of \( p  \) contains infinitely many points of \( E  \)
\end{theorem}

\begin{proof}
Suppose for sake of contradiction that there exists a neighborhood of \( p  \) that contains finitely many points of \( E  \); that is,
\begin{center}
    \( \exists \epsilon > 0  \) such that \( {N}_{\epsilon}(p) \cap E  \) is a finite set.
\end{center}
Since \( {N}_{\epsilon}(p) \cap (E \setminus  \{ p \} ) \subseteq  {N}_{\epsilon}(p) \cap E  \), we can immediately conclude that \( {N}_{\epsilon}(p) \cap (E \setminus  \{ p \} ) \) is finite also. Furthermore, \( {N}_{\epsilon}(p) \cap (E \setminus  \{ p  \} ) \) is nonempty since \( p \in E' \). Let us denote the elements of \( {N}_{\epsilon}(p) \cap (E \setminus  \{ p \} )  \) by \( {x}_{1}, \dots, {x}_{n} \). Our goal is to find a \( \delta > 0  \) such that the neighborhood with radius \( \delta > 0  \), we will not contain any of the finite points we introduced. For each \( i \in \{ 1,\dots, n \}  \), \( d(p,{x}_{i}) > 0  \),
\[  \delta = \min \{ d(p,{x}_{i}) : i \in {1,\dots,n} \} > 0.   \]
Clearly, \( {N}_{\delta/2}(p) \cap (E \setminus  \{ p \} ) = \emptyset \). But this contradicts our assumption that \( p  \) is NOT a limit point of \( E  \).
\end{proof}

\begin{corollary}
    A finite set has no limit points; that is, if \( E  \) is finite, then \( E' = \emptyset \).
\end{corollary}

\begin{proof}
This is just the contrapositive of the theorem above.
\end{proof}

\begin{theorem}[ ]
  Let \( (X,d) \) be a metric space and \( E \subseteq X  \). We have that \( E  \) is open if and only if \( E^{c} \) closed.
\end{theorem}

\begin{proof}
\( (\Longrightarrow) \) Assume that \( E  \) is open. We want to show that \( E^{c} \) is closed; that is, every limit point of \( E^{c} \) is contained in \( E^{c} \). Let \( p  \) be a limit point of \( (E^{c}) \). Assume for sake of contradiction that \( p \notin E^{c} \). Then \( p \in E  \). Since \( E  \) is open, \( p  \) is an interior point of \( E  \). Thus, there exists \( \delta > 0  \) such that \( {N}_{\delta}(p) \subseteq E  \); that is, there exists \( \delta > 0  \) such that \( {N}_{\delta}(p) \cap E^{c} = \emptyset \). Furthermore, we have that 
\[  {N}_{\delta}(p) \cap (E^{c} \setminus  \{ p \} ) = \emptyset. \]
But this tells us that \( p \) is not a limit point which is a contradiction.

\( (\Longleftarrow) \) Assume that \( E^{c} \) is closed. We want to show that \( E  \) is open; that is, every \( x \in E  \) is an interior point. Let \( p \in E  \). Assume for sake of contradiction that \( p \notin E^{\circ} \). Then for all \( \delta > 0  \), \( {N}_{\delta}(p) \not\subseteq E\). Hence, for all \( {N}_{\epsilon}(p) \cap E^{c} \neq \emptyset \). Therefore, 
\[  \forall \delta > 0 \ {N}_{\delta} (p) \cap (E^{c} \setminus  \{ p \} ) \neq \emptyset. \]
That is, \( p  \) is a limit point of \( E^{c} \). But by assumption, \( E^{c} \) is closed. Thus, \( p \in E^{c} \). But this contradicts the assumption that \( p \in E  \).
\end{proof}

\begin{theorem}[ ]
    Let \( (X,d) \) be a metric space. Let \( \{ {A}_{\alpha} \}_{\alpha \in \Lambda} \) be a collection of open sets where \( \Lambda  \) is an index set (can be finite or infinite). Then     
    \[  \bigcup_{ \alpha \in \Lambda }^{  }  {A}_{\alpha} \]
    is an open set.
\end{theorem}
\begin{proof}
Our goal is to show that every point of \( A =  \bigcup_{ \alpha \in \Lambda }^{  } {A}_{\alpha}  \) is an interior point. Let \( p \in A   \). Thus, there exists \( \alpha \in \Lambda \) such that \( p \in {A}_{\alpha} \). Since \( {A}_{\alpha} \) is open, so there exists \( \delta > 0  \) such that \( {N}_{\delta}(p) \subseteq  {A}_{\alpha} \). But note that 
\[  {A}_{{\alpha}_{0}} \subseteq  A.  \]
Hence, 
\[  {N}_{\delta}(p) \subseteq A  \]
and thus \( p  \) is an interior point of \( A  \).

\end{proof}

\begin{theorem}[ ]
    Let \( {A}_{1}, \dots, {A}_{n} \) be open sets in the metric space \( (X,d) \). Then
    \[  \bigcap_{ k = 1  }^{ n }  {A}_{k} \ \text{is open}. \]
\end{theorem}
\begin{proof}
Our goal is to show that every point of \( \bigcap_{ k = 1  }^{ n  }  {A}_{k } \) is an interior point of \( \bigcap_{ k = 1  }^{ n }  {A}_{k } \). Let \( p \in \bigcap_{  k = 1  }^{ n }  {A}_{k } \). Then for all \(  1 \leq k \leq n  \) such that \( p \in {A}_{k} \). Since \( {A}_{k} \) is open for all \( k  \), we know that for all \( 1 \leq k \leq n   \), there exists \( {\delta}_{k} > 0  \) such that \( {N}_{{\delta}_{k }} (p) \subseteq {A}_{k} \). Let \( \delta = \min \{ {\delta}_{i} : 1 \leq i \leq n   \}  \). Then we have that  
\[  {N}_{\delta}(p) \subseteq  {N}_{{\delta}_{k }}(p) \subseteq  {A}_{k}. \]
Consequently, we have 
\[  {N}_{\delta}(p) \subseteq  \bigcap_{  k = 1 }^{ n }  {A}_{k}. \]
Hence, \( p  \) is an interior point of the intersection \( \bigcap_{  k = 1  }^{ n }  {A}_{k} \).
\end{proof}


\begin{theorem}[ ]
Let \( (X,d) \) be a metric space and \( E \subseteq X  \).
\begin{enumerate}
    \item[(1)] \( \overline{E} \) is a closed set. 
    \item[(2)] \( E  \) is closed if and only if \( E = \overline{E} \).
    \item[(3)] If \( E \subseteq F  \) and \( F \) is closed, then \( \overline{E} \subseteq F  \).
\end{enumerate}
\end{theorem}
\begin{proof}
Our goal is to show that \( (\overline{E})^{c} \) is open. We need to show that every point of \( (\overline{E})^{c} \) is an interior point of \( (\overline{E})^{c} \). Let \( p \in (\overline{E})^{c} \). We have 
\begin{align*}
    p \in (\overline{E})^{c} &\Longrightarrow p \notin \overline{E} \\ 
                             &\Longrightarrow p \notin (E \cup E') \\
                             &\Longrightarrow p \notin E \ \wedge \ p \notin E'.
\end{align*}
Note that 
\begin{align*}
    p \notin E' &\Longrightarrow \exists \epsilon > 0 \ {N}_{\epsilon}(p) \cap (E \setminus \{ p \} ) = \emptyset \\
                &\Longrightarrow \exists \epsilon > 0 \ {N}_{\epsilon}(p) \cap E = \emptyset. \tag{1}
\end{align*}
In what follows, we will show that \( {N}_{\epsilon}(p) \cap E' = \emptyset \). So, we have
\begin{align*}
    &{N}_{\epsilon}(p) \cap (E \cup E') = \emptyset \\
                                       &\Longrightarrow {N}_{\epsilon}(p) \cap \overline{E} = \emptyset \\
                                       &\Longrightarrow {N}_{\epsilon}(p) \subseteq (\overline{E})^{c}.
\end{align*}
Thus, we have that \( p  \) is an interior point of \( (\overline{E})^{c}\). It remains to show that \( {N}_{\epsilon}(p) \cap E'  = \emptyset\). Assume for sake of contradiction that \( {N}_{\epsilon}(p) \cap E' \neq \emptyset \). Let \( q \in {N}_{\epsilon}(p) \cap E' \). Then we have \( q \in {N}_{\epsilon}(p)  \) and \( q \in E' \). Hence, there exists \( \delta > 0  \) such that \( {N}_{\delta}(q) \subseteq {N}_{\epsilon}(p) \) and that \( {N}_{\delta}(q) \cap (E \setminus  \{ q \} ) \neq \emptyset \), respectively. But note that since \( {N}_{q}(p) \subseteq  {N}_{\epsilon}(p)  \) and \( E \setminus  \{ q  \} \subseteq E   \) implies that 
\[  {N}_{\epsilon}(p) \cap E \neq \emptyset \]
which contradicts (1).
\end{proof}

\begin{definition}[Metric Subspace]
    Let \( (X,d) \) be a metric space and let \( Y  \) be a nonempty subset of \( X  \). Then \( (Y, d |_{Y \times Y}) \) is called a \textbf{metric subspace} of \( (X,d) \).
\end{definition}

\begin{remark}
    Consider the metric subspace \( (Y, d |_{Y \times Y} \) of \( (X,d) \). Let \( p \in Y  \) and \( \epsilon > 0  \). Then we define
    \begin{align*} {N}_{\epsilon}^{Y}(p) = \{ y \in Y : d^{Y}(y,p) < \epsilon \} &= \{ y \in Y : d(y,p) < \epsilon \}   \\
        &= {N}_{\epsilon}(p) \cap Y.
    \end{align*}
\end{remark}


\end{document}
