\section{Continuous Functions}

\subsubsection{Exercise 4.3.1} Let \( g(x) = \sqrt[3]{x }  \).
\begin{enumerate}
    \item[(a)] Prove that \( g \) is continuous at \( c = 0  \).
        \begin{proof}
            Let \( \epsilon > 0  \). Suppose \( c = 0  \). Let \( c \in A  \) and \( g(x) = \sqrt[3]{ x }  \). Since \( | x | < \delta  \), we can say that \( |\sqrt[3]{ x }| < \sqrt[3]{ \delta }   \). Then choose \( \delta = \epsilon^3 \) such that 
            \begin{align*}
                | g(x)  - g(c) | &= | \sqrt[3]{ x } - 0  |  \\
                                 &= | \sqrt[3]{ x }  |  \\
                                 &< \sqrt[3]{ \epsilon^3 } \\
                                 &= \epsilon.
            \end{align*}
            Hence, we have that 
            \[  \lim_{ x \to 0 } \sqrt[3]{ x } = 0 . \]
        \end{proof}
    \item[(b)] Prove that \( g  \) is continuous at a point \( c \neq 0  \). (The identity \( a^3 - b^3 = (a-b)(a^2 + ab + b^2)  \) will be helpful.)
        \begin{proof}
        Now let \( c \neq  0  \). Let \( \epsilon > 0  \) and suppose \( | x - c  | < \delta \). By the given identity \( a^3 - b^3 = (a-b)(a^2 +ab +b^2) \), we can write 
        \begin{align*}
            | g(x) - g(c) | &= | \sqrt[3]{x} - \sqrt[3]{c}     |  \\
                            &= \Big| x^{3/9} - c^{3/9} \Big| \\  
                            &= | x^{1/9} - c^{1/9} | | x^{2/9} + x^{2/9}c^{2/9} + c^{2/9} |.
        \end{align*}
        Since \( | x - c  | < \delta \), we have 
        \begin{align*}
            x^{1/9} - c^{1/9}  &< (\delta + c)^{1/9} - c^{1/9} \tag{1}  \\
            x^{2/9} +x^{1/9}c^{1/9} + c^{2/9}  &< (\delta + c )^{2/9} + x^{1/9}c^{1/9} + c^{1/9} \tag{2} \\
            x^{1/9} c^{1/9} &< (\delta + c )^{1/9} c^{1/9} \tag{3}.
        \end{align*}
        By using the identity again, we write
        \begin{align*}
            | g(x) - g(c) | &= | x^{1/9} - c^{1/9} | | x^{2/9} + x^{2/9}c^{2/9} + c^{2/9} |  \\
                            &< [(\delta + c)^{1/9} - c^{1/9} ] [(\delta + c )^{2/9} + (\delta + c )^{1/9} c^{1/9} + c^{1/9}] \\
                            &= (\delta + c )^{3/9} - c^{3/9}  \\  
                            &= (\delta + c)^{1/3} - c^{1/3}.  \tag{4} \\
        \end{align*}
        Now let \( \delta = \min \{ \delta_1, \delta_2  \}  \) such that (4) implies
        \[ (\delta + c)^{1/3} - c^{1/3} = (\delta^3 - c + c )^{1/3} - c^{1/3} = \epsilon + c^{1/3} - c^{1/3} = \epsilon. \]
        Hence, we have \( | g(x) - g(c) | < \epsilon  \) implying that
        \[ \lim_{ x \to c } g(x) = g(c). \] 
        \end{proof}
\end{enumerate}

\subsubsection{Exercise 4.3.3} 
\begin{enumerate}
    \item[(a)] Supply a proof for Theorem 4.2.3 using the \( \epsilon - \delta \) characterization of continuity.
        \begin{proof}
        Let \( f: A \to \R  \) and \( g: B \to \R  \). Assume that the range 
        \[  f(A) = \{ f(x) : x \in A  \}  \] is contained in the domain \( B  \) so that the composition \( g \circ f (x) = g(f(x)) \) is defined on \( A  \). Suppose \( f  \) is continuous at \( c \in A  \) and \( g  \) is continuous at \( f(c) \in B  \). Let \( \epsilon > 0  \). Since \( f \) is continuous at \( c \in  A  \), we can construct \( \delta > 0  \) such that  \( | x - c | < \delta  \) where
        \[ | f(x) - f(c)   | < \epsilon. \] Let \( \epsilon  = \delta  \). Then assume 
        \[ | f(x) - f(c)  | < \delta \] since \( g \) is continuous at \( f(c) \in B  \). Then we immediately have that 
        \[ | g \circ f (x) - g \circ f(c) | = | g(f(x)) - g(f(c)) | < \epsilon. \]
        Hence, we have 
        \[  \lim_{ x  \to c } g \circ f (x) = g \circ f(c). \]
        \end{proof}
    \item[(b)] Give another proof of this theorem using the sequential characterization of continuity.
        \begin{proof}
        Let \( f(x_n) \subseteq f(A) \) and \( (x_n) \subseteq A \) where the image 
        \[ f(A) = \{ f(x) : x \in A  \} .\]
        Let \( \epsilon > 0  \). Since \( (x_n) \to c  \), there exists \( N \in \N  \) such that for any \( n \geq N  \), we have 
        \[  | f(x_n)  - f(c)| < \epsilon. \]
        But \( g(f(x_n0) \to g(f(c)) \) since \( g \) is continuous at \( f(c)\in B  \) so we end up having 
        \begin{align*}
           | g \circ f(x_n) - g \circ f(c) |  &= |  g(f(x_n)) - g(f(c))| < \epsilon.
        \end{align*}
        Hence, we have 
        \[ \lim g \circ f(x_n) = g \circ f (c).  \]
        Note that this fact follows immediately if \( f(x_n) = f(c) \) and \( x_n = c  \).
        \end{proof}
\end{enumerate}


\subsubsection{Exercise 4.3.5} Show using definition 4.3.1 that if \( c \) is an isolated point of \( A \subseteq \R  \), then \( f: A \to \R  \) is continuous at \( c \).
\begin{proof}
    Since \( c \in A  \) and \( c  \) is an isolated point of \( A \subseteq \R  \), we must have \( x = c  \) and \( f(x) = f(c) \) where \( x \in A  \) is an arbitrary point. This follows from the fact that there exists an \( \epsilon - \)neighborhood such that \( V_{\epsilon }(x) \cap A = \emptyset \). Let \( \epsilon > 0  \). Then choose \( \delta = \epsilon  \) such that whenever \( | x - c  | < \delta \), we have that 
\[ | f(x) - f(c) | = | f(c) - f(c) | = 0 < \epsilon. \]
\end{proof}

\subsubsection{Exercise 4.3.6} Using the \( \epsilon - \delta \) characterization of continuity (and thus using no previous results about sequences), show that the linear function \( f(x) = ax + b  \) is continuous at every point \( x \in \R  \).
\begin{proof}
Let \( \epsilon > 0  \) and let \( c \in \R  \) be arbitrary. Choose \( \delta = \epsilon  / a  \) such that whenever \( | x - c  | < \delta  \), we have that 
\begin{align*}
   | f(x) - f(c) |  &= |  (ax + b ) - (ac + b ) |  \\
                    &= | a ( x - c ) | \\
                    &= a | x - c  | \\
                    &< a \cdot \frac{ \epsilon  }{ a  } \\
                    &= \epsilon.
\end{align*}
Hence, every linear function \( f(x) = ax + b  \) is continuous at any point \( c \in \R  \).
\end{proof}


\subsubsection{Exercise 4.3.7} Assume \( h: \R \to \R  \) is continuous on \( \R  \) and let \( K = \{ x : h(x) = 0  \}  \). Show \( K \) is a closed set.
\begin{proof}
Let \( h: \R \to \R  \) be a continuous function on \( \R  \).  Let \( c \in K  \). Since \( h \) is continuous on \( \R  \) we can use the Sequential Criterion. Let \( x_n \in K  \). There exists  \( (x_n) \subseteq K\) such that \( (x_n) \to  c \) implying that \( h(x_n) \to h(c) \). Since every \( x \in K  \) has the property that \( h(x) = 0  \) and \( c \in K  \), we have that \( h(c) = 0  \). Hence, \( h(x_n) \to h(c) \) is contained in \( K \). Thus, \( K \) is closed. 
\end{proof}







\subsubsection{Exercise 4.3.10} Observe that if \( a  \) and \( b  \) are real numbers, then 
\[  \max \{ a,b  \} = \frac{ 1 }{ 2 } [ (a+b) + | a - b  | ]. \]

\begin{enumerate}
    \item[(a)] Show that if \( f_1, f_2, \dots, f_n  \) are continuous functions, then 
        \[ g(x) = \max \{ f_1(x), f_2(x), \dots f_n(x) \}  \]
        is a continuous function.
        \begin{proof}
        Suppose \( f_1, f_2, \dots, f_n  \) are continuous functions. We proceed by inducting on \( n  \). Let our base case be \( n = 2  \). Then we have our continuous functions \( f_1, f_2  \). By using the \( \epsilon -\delta \) definition for continuity, we have that 
        \begin{align*}
            | g(x) - g(c) | &= \Big| \frac{ 1 }{ 2 } \Big[ (f_1(x) + f_2(x)) + | f_1(x) - f_2(x) |  \Big] \\
                            &- \frac{ 1 }{ 2 } \Big[ (f_1(c) + f_2(c)) + | f_1(c) - f_2(c) |  \Big] \Big|  \\
                            &= \Big| \frac{ 1 }{ 2 } \Big[  (f_1(x) - f_1(c)) + (f_2(x) - f_2(c))    \Big] \\  &+ \frac{ 1 }{ 2 } \Big[ |f_1(x) - f_2(x)| + | f_1(c) - f_2(c) |  \Big] \Big| \\
                            &\leq \frac{ 1 }{ 2 } \Big[ | f_1(x) - f_1(c)  | + | f_2(x) - f_2(c) |  \\ 
                            &+ | (f_1(x) - f_2(x)) - (f_1(c) -f_2(c))| \Big] \\
        \end{align*}
        \end{proof}
\end{enumerate}









\subsubsection{Exercise 4.3.11 (Contraction Mapping Theorem).} Let \( f  \) be a function defined on all of \( \R  \), and assume there is a constant \( c  \) such that \(  0 < c < 1 \) and 
\[  | f(x) - f(y) | \leq c | x - y |  \]
for all \( x,y \in \R  \).

\begin{enumerate}
    \item[(a)] Show that \( f  \) is continuous on \( \R  \).
        \begin{proof}
        Let \( f: \R  \to \R  \) and let \( x,c \in \R   \) where \( c  \) is a limit point of \( A  \). We want to show that \( f \) is continuous on \( \R  \); that is, we want to show that 
        \[  \lim_{ x \to c } f(x) = f(c). \]
        Let \( \epsilon > 0  \). Choose \( \delta = \epsilon / c  \) such that whenever \( | x - c  | < \delta \) we have 
        \[  | f(x) - f(c) | \leq k | x - c  | < k \cdot \frac{ \epsilon  }{ k } = \epsilon. \]
        Hence, we have 
        \[ \lim_{ x \to c } f(x) = f(c). \]
        \end{proof}
    \item[(b)] Pick some point \( y_1 \in \R  \) and construct the sequence 
        \[  (y_1, f(y_1), f(f(y_1)), ...).\]
        In general, if \( y_{n+1} = f(y_n) \), show that the resulting sequence \( (y_n) \) is a Cauchy sequence. Hence, we may let \( y = \lim y_n \).
        \begin{proof}
        Observe that for any fixed \( n \in \N  \), 
        \[ | y_{m+1} - y_{m+1} | = | f(y_m) - f(y_{m+1}) | \leq c | y_m - y_{m_+1} |. \] We can show this via induction that 
        \begin{align*}
            | y_{m+1} - y_{m+2} | &\leq c | y_{m} - y_{m+1}  |  \\
                                  &\leq c^2 | y_{m-1} - y_m | \\
                                  &\vdots \\
                                  &\leq c^m | y-1 - y_2 |.
        \end{align*}
        The fact that \( 0 < c <  1 \) means that \( \sum_{ n=1 }^{ \infty  } c^n  \) converges (because it is a geometric series) enables us to conclude that \( (y_n) \) is Cauchy sequence. To see this, observe that 
        \begin{align*}
            | y_m  - y_n  | &= | y_m - y_{m+1} + y_{m+1} + \dots + y_{n-1} - y_n |  \\
                            &\leq c^{m-1} | y_1 - y_2  | + c^m | y_1 - y_2  | + \dots c^{n-2} | y_1 - y_2  | \\ 
                            &= c^{m-1} | y_1 - y_2  | (1 + c + \dots + c^{n - m - r }) \\
                            &< c^{m-1} | y_1 - y_2  | \Big( \frac{ 1 }{ 1 - c  }  \Big).
        \end{align*}
    Let \( \epsilon > 0  \), and choose \( N \in \N  \) large enough so that \( c^{N-1} < \epsilon 1 - c / | y_1 - y_2  |   \). Then the previous calculation shows that \( n > m \geq N  \) implies \( | y_m - y_n  | < \epsilon  \); that is, we have
    \begin{align*}
        | y_{m+1} - y_{n+1} | &\leq | y_m - y_n  |  \\
                            &< c^{N-1} | y_1 - y_2  | \Big( \frac{ 1 }{ 1 - c  }   \Big) \\
                            &< \frac{ \epsilon (1 - c ) }{ | y_1 - y_2  |  } \cdot \frac{ | y_1 - y_2  |  }{ 1 -c  } \\ 
                            &= \epsilon.
    \end{align*}
    Hence, \( (y_n) \) is Cauchy Sequence.
\end{proof}
\item[(c)] Prove that \( y  \) is a fixed point of \( f \); that is, \( f(y) = y  \) and that it is unique in this regard.
    \begin{proof}
    Since \( f  \) is continuous on \( \R  \) and \( (y_n) \subseteq \R  \) is a Cauchy sequence and that \( \lim y_n = y  \) for all \( n \in \N  \), we have that 
    \[ f(y_n) = y_{n+1} \to f(y) = y.  \]
    Hence, \( y \) is a fixed point of \( f \).
    \end{proof}
    \item[(d)] Finally, prove that if \( x \) is \textit{any} arbitrary point in \( \R  \) then the sequence \( (x, f(x), f(f(x)),...) \) converges to \( y \) defined in (b).
        \begin{proof}
            Let us fix \( x \in \R  \) where \( (x_n) \subseteq \R  \) is a sequence of points. Since the \( f \) is defined like  \( f(x_{n}) = x_{n+1}   \). Since \( x \in \R  \) is fixed, we know that \( f(x_n) \to f(x) \) and that \( (x_{n+1}) \to  x  \). Hence, \( f(x) = x  \) as defined in (b). 
        \end{proof}
\end{enumerate}


\subsubsection{Exercise 4.3.12} Let \( F \subseteq \R  \) be a nonempty closed set and define \( g(x) = \inf \{ | x - a  | : a \in  F  \}  \). Show that \( g \) is continuous on all of \( \R  \) and \( g(x) \neq  0 \) for all \( x \notin F  \).
\begin{proof}
Let \( F \subseteq \R  \) be a nonempty closed set. Let \( x \in F  \). Since \( F \) is a closed, let \( (x_n)  \) be a Cauchy sequence such that \( (x_n) \to x  \) that is contained in \( F \). But since \( g: F \to \R  \), we must have 
\[ | g(x_n) - g(x) | < \epsilon \]
by the Sequential Criterion of Continuity. This means \( g \) is continuous on all of \( \R  \).

Let \( x \notin F  \). Suppose for sake of contradiction that \( g(x) = 0  \). Let \( (x_n) \subseteq F  \) where \( x_n \in F  \). Since \( F  \) is closed, \( (x_n) \) is a Cauchy sequence such that \( (x_n) \to x  \). But since \( g \) is continuous \( x  \) has to be contained in \( F  \) which is a contradiction. Hence, it must be that \( g(x) \neq 0  \).
\end{proof}









\subsubsection{Exercise 4.3.13} Let \( f \) be a function defined on all of \( \R  \) that satisfies the additive condition \( f(x+y) = f(x) + f(y) \) for all \( x,y \in \R  \).
\begin{enumerate}
    \item[(a)] Show that \( f(0) = 0  \) and that \( f(-x) = - f(x) \) for all \( x \in \R  \).
        \begin{proof}
        By using the linearity property of \( f \), we have \( f(0 + 0) = f(0) + f(0)  \) which implies \( f(0) = 0 \). For the inverse property, suppose \( x \in \R  \) such that \( x + (-x) = 0  \). Then using the linearity property of \( f \), we have \( f(x) + (-x)) = f(x) + f(-x)   \). Since \( f(0) = 0  \), we have that \( f(x) + f(-x) \) implies \( f(-x) = -f(x)   \).
        \end{proof}
    \item[(b)] Let \( k = f(1) \). Show that \( f(n) = k n \) for all \( n \in \N  \), and then prove that \( f(z) = kz \) for all \( z \in \Z  \). Now, prove that \( f(r) = kr \) for any rational number \( r \).
        \begin{proof}
        Let \( k = f(1) \). We proceed to show \( f(n) = kn \) by inducting on \( n \in \N  \). Let our base case be \( n = 1  \). If \( n = 1  \), then \( f(1) =  k \). Now suppose \( f(n) \) holds for \( 1 \leq n \leq \ell - 1  \). Then 
        \begin{align*}
           f(\ell) &= k \ell \\
                   &= k (\ell + 1 - 1 ) \\
                   &= k(\ell - 1) + k \\
                   &= f(\ell - 1 ) + f(1).
        \end{align*}
        Hence, \( f(n) = kn \) for all \( n \in \N  \). To prove \( f(z) = kz \) for all \( z \in \ Z \) we can just prove it for all negative integers and zero. This is easy to see when \( z = 0  \). It's also easy to see that \( f \) holds for \( z \in \Z^{-} \). Since \( f(-x) = -f(x) \), we have that \( f(-\ell) = - f(\ell) \). Since \( f(n)  \) holds for all \( n \in \Z^{+} \). Hence, \( f(z) = nz \) for all \( z \in \Z \). 
    Before proving \( f(r) = kr  \) for any rational number \( r  \), let us consider \( 1/n  \) where \( n \in \N  \). Note that 
    \begin{align*}
         k &= f(1)  \\
           &= f \Big( \frac{ 1 }{ n } + \frac{ 1 }{ n }  + \dots + \frac{ 1 }{ n }  \Big) \\
           &= n f \Big( \frac{ 1 }{ n }  \Big).
    \end{align*}
    Applying this for any given \( r \in \Q  \), we can see that 
    \begin{align*}
        f(m/n) &= f \Big( \frac{ 1 }{ n } + \frac{ 1 }{ n } + \dots + \frac{ 1 }{ n }  \Big) \\
               &= m f \Big( \frac{ 1 }{ n }  \Big) \\ 
               &= k \Big( \frac{ m }{ n }  \Big). \\
    \end{align*}
    We can prove that this holds for any rational number \( r < 0  \) by using a similar strategy to the used to prove the negative integers case above.
        \end{proof}
    \item[(c)] Show that if \( f \) is continuous at \( x = 0  \), then \( f \) is continuous at every point in \( \R  \) and conclude that \( f(x) = k x  \) for all \( x \in \R  \). Thus, any additive function that is continuous at \( x = 0  \) must necessarily be a linear function through the origin.
        \begin{proof}
        Assume \( f \) is continuous at \( x = 0  \). Let \( \epsilon > 0  \). Choose \( \delta = \epsilon / k  \) such that whenever \( | x - c  | < \delta  \), we have that 
        \begin{align*}
            | f(x) - f(c) | &= | kx - kc  |  \\
                            &= k | x - c  | \\
                            &< k \cdot \frac{ \epsilon  }{  k } \\
                            &= \epsilon.
        \end{align*}
        Hence, \( f  \) is continuous for \( c \neq 0  \). But \( f \) is also continuous at \( x = 0  \). Hence, \( f \) is continuous at every point in \( \R  \) and thus \( f(x) = kx \) for all \( x \in \R  \).
        \end{proof}
\end{enumerate}






































 
